---
title: "NEPHU First Nations Population Profile"
subtitle: "Population: Population Size"
output:
  officedown::rdocx_document:
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "04A Population Size ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
# 
source(here::here("Code", "00_Setup.R"))

source(here::here("Code", "Functions", "Data prep", "f_read_census_population.R"))

source(here::here("Code", "Functions", "Graphs", "f_graph_lga.R"))

source(here::here("Code", "Functions", "Tables", "f_table_population.R"))
```


```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 4A-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 4A-"))
  
  return(caption)
  
}
```

### How many Aboriginal and/or Torres Strait Islander population live in the NEPHU catchment and where do they reside?

# Population Size

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Total population by Aboriginality, with age, sex, and LGA breakdowns
# Data from ABS Census
# ------------------------------------------------------------------------------
# Read in Census data
aboriginal_lga <- f_read_census_population(table = "G07", 
                                           level = "lga")

# Join to LPHU reference table
aboriginal_lga <- aboriginal_lga %>% 
  dplyr::left_join(lphu_assign, by = "LGA_CODE_2021") %>% 
  #
  janitor::clean_names()

# Aboriginal and non-Aboriginal peoples in each LPHU
results <- list()

for (i in lphu_names_short) {
  
  results[[i]] <- aboriginal_lga %>% 
    dplyr::filter(lphu_short == i) %>% 
    #
    janitor::adorn_totals(name = i,
                          fill = i) %>% 
    #
    dplyr::mutate(
      lga_id = dplyr::case_when(
        lga_code_2021 == i ~ i,
        #
        TRUE ~ as.character(lga_id)))
  
  }

# Bind LPHU and Victorian data
aboriginal_lga <- results[["NEPHU"]] %>% 
  dplyr::bind_rows(results[["SEPHU"]]) %>%
  dplyr::bind_rows(results[["WPHU"]]) %>% 
  dplyr::bind_rows(results[["BSWPHU"]]) %>% 
  dplyr::bind_rows(results[["LMPHU"]]) %>% 
  dplyr::bind_rows(results[["GPHU"]]) %>% 
  dplyr::bind_rows(results[["GWSMPHU"]]) %>% 
  dplyr::bind_rows(results[["GVPHU"]]) %>% 
  dplyr::bind_rows(results[["OMPHU"]]) %>% 
  dplyr::bind_rows(aboriginal_lga %>% 
                     janitor::adorn_totals(name = "VIC",
                                           fill = "VIC") %>% 
                     #
                     dplyr::mutate(lga_id = dplyr::case_when(
                       lga_code_2021 == "VIC" ~ "VIC",
                       #
                       TRUE ~ as.character(lga_id))) %>% 
                     #
                     dplyr::filter(lga_code_2021 == "VIC"))

# Tidy up environment
rm(i, results)

# ------------------------------------------------------------------------------
# Total population by Aboriginality, by LPHU
# Data from ABS Census
# ------------------------------------------------------------------------------
population_lphu <- aboriginal_lga %>%
  dplyr::filter(lga_name %in% lphu_names_short) %>% 
  #
  dplyr::mutate(
    aboriginal_prop          = (tot_indigenous_p / tot_tot_p) * 100,
    aboriginal_prop_per_lphu = tot_indigenous_p / sum(tot_indigenous_p) * 100,
    #
    non_aboriginal_n             = tot_non_indigenous_p + tot_indig_status_ns_p,
    non_aboriginal_prop          = (non_aboriginal_n / tot_tot_p) * 100,
    non_aboriginal_prop_per_lphu = non_aboriginal_n / sum(non_aboriginal_n) * 100) %>% 
  #
  dplyr::bind_rows(aboriginal_lga %>% 
                     dplyr::filter(lga_name == "VIC") %>%
                     #
                     dplyr::mutate(
                       aboriginal_prop          = (tot_indigenous_p / tot_tot_p) * 100,
                       aboriginal_prop_per_lphu = tot_indigenous_p / sum(tot_indigenous_p) * 100,
                       #
                       non_aboriginal_n             = tot_non_indigenous_p + tot_indig_status_ns_p,
                       non_aboriginal_prop          = (non_aboriginal_n / tot_tot_p) * 100,
                       non_aboriginal_prop_per_lphu = non_aboriginal_n / sum(non_aboriginal_n) * 100)) %>% 
  #
  dplyr::select(lphu_name = lga_name,
                aboriginal_n = tot_indigenous_p,
                aboriginal_prop,
                aboriginal_prop_per_lphu,
                non_aboriginal_n = tot_non_indigenous_p,
                non_aboriginal_prop,
                non_aboriginal_prop_per_lphu)

# ------------------------------------------------------------------------------
# Total population by Aboriginality, by LGA
# Data from ABS Census
# ------------------------------------------------------------------------------
population_lga <- aboriginal_lga %>%
  dplyr::filter(lphu_short == "NEPHU" & lga_name != "NEPHU") %>% 
  #
  dplyr::mutate(
    aboriginal_prop         = (tot_indigenous_p / tot_tot_p) * 100,
    aboriginal_prop_per_lga = tot_indigenous_p / sum(tot_indigenous_p) * 100,
    #
    non_aboriginal_n            = tot_non_indigenous_p + tot_indig_status_ns_p,
    non_aboriginal_prop         = (non_aboriginal_n / tot_tot_p) * 100,
    non_aboriginal_prop_per_lga = non_aboriginal_n / sum(non_aboriginal_n) * 100) %>% 
  #
  dplyr::bind_rows(aboriginal_lga %>% 
                     dplyr::filter(lga_name == "NEPHU") %>% 
                     #
                     dplyr::mutate(
                       aboriginal_prop         = (tot_indigenous_p / tot_tot_p) * 100,
                       aboriginal_prop_per_lga = tot_indigenous_p / sum(tot_indigenous_p) * 100,
                       #
                       non_aboriginal_n            = tot_non_indigenous_p + tot_indig_status_ns_p,
                       non_aboriginal_prop         = (non_aboriginal_n / tot_tot_p) * 100,
                       non_aboriginal_prop_per_lga = non_aboriginal_n / sum(non_aboriginal_n) * 100)) %>% 
  #
  dplyr::select(lga_name,
                aboriginal_n = tot_indigenous_p,
                aboriginal_prop,
                aboriginal_prop_per_lga,
                non_aboriginal_n = tot_non_indigenous_p,
                non_aboriginal_prop,
                non_aboriginal_prop_per_lga)

# ------------------------------------------------------------------------------
# Total population by Aboriginality, by SA2
# Data from ABS Census
# ------------------------------------------------------------------------------
# Read in Census data
aboriginal_sa2 <- f_read_census_population(table = "G07",
                                           level = "sa2") %>% 
  janitor::clean_names() %>% 
  #
  dplyr::mutate(sa2_code_2021 = as.character(sa2_code_2021))
  
aboriginal_sa2 <- aboriginal_sa2 %>% 
  dplyr::bind_rows(aboriginal_sa2 %>% 
                     dplyr::filter(sa2_code_2021 %in% nephu_sa2) %>% 
                     #
                     janitor::adorn_totals(name = "NEPHU") %>% 
                     #
                     dplyr::filter(sa2_code_2021 == "NEPHU"))

# Data wrangling
population_sa2 <- aboriginal_sa2 %>%
  dplyr::filter(sa2_code_2021 %in% nephu_sa2) %>% 
  #
  dplyr::mutate(
    aboriginal_prop         = (tot_indigenous_p / tot_tot_p) * 100,
    aboriginal_prop_per_sa2 = tot_indigenous_p / sum(tot_indigenous_p) * 100,
    #
    non_aboriginal_n            = tot_non_indigenous_p + tot_indig_status_ns_p,
    non_aboriginal_prop         = (non_aboriginal_n / tot_tot_p) * 100,
    non_aboriginal_prop_per_sa2 = non_aboriginal_n / sum(non_aboriginal_n) * 100) %>% 
  #
  dplyr::bind_rows(aboriginal_sa2 %>% 
                     dplyr::filter(sa2_code_2021 == "NEPHU") %>% 
                     #
                     dplyr::mutate(
                       aboriginal_prop         = (tot_indigenous_p / tot_tot_p) * 100,
                       aboriginal_prop_per_sa2 = tot_indigenous_p / sum(tot_indigenous_p) * 100,
                       #
                       non_aboriginal_n            = tot_non_indigenous_p + tot_indig_status_ns_p,
                       non_aboriginal_prop         = (non_aboriginal_n / tot_tot_p) * 100,
                       non_aboriginal_prop_per_sa2 = non_aboriginal_n / sum(non_aboriginal_n) * 100)) %>% 
  #
  dplyr::left_join(nephu_sa2.sf %>% 
                     dplyr::select(sa2_code, sa2_name),
                   by = c("sa2_code_2021" = "sa2_code")) %>% 
  #
  dplyr::select(sa2_code_2021,
                sa2_name,
                aboriginal_n = tot_indigenous_p,
                aboriginal_prop,
                aboriginal_prop_per_sa2,
                non_aboriginal_n,
                non_aboriginal_prop,
                non_aboriginal_prop_per_sa2)

# ------------------------------------------------------------------------------
# Population density, by LGA
# Data from ABS Census
# ------------------------------------------------------------------------------
density_lga <- dplyr::left_join(nephu_lga.sf, 
                                aboriginal_lga %>% 
                                  dplyr::select(lga_name, tot_indigenous_p),
                                by = "lga_name") %>%
  #
  dplyr::mutate(pop_dens       = round(tot_indigenous_p / areasqkm, 1), 
                pop_dens_label = paste0(lga_name, "\n(", pop_dens, ")"))

# ------------------------------------------------------------------------------
# Population density, by SA2
# Data from ABS Census
# ------------------------------------------------------------------------------
density_sa2 <- dplyr::left_join(nephu_sa2.sf, 
                                aboriginal_sa2 %>% 
                                  dplyr::select(sa2_code_2021, tot_indigenous_p),
                                by = c("sa2_code" = "sa2_code_2021")) %>%
  #
  dplyr::mutate(pop_dens = round(tot_indigenous_p / sa2_area, 1))
```

::: {custom-style="Dotpt"}
- NEPHU has the largest number of residents who identified as Aboriginal and/or Torres Strait Islander in the 2021 Census for the state of Victoria (n = 12,065), representing 0.7% of the NEPHU catchment population.

- 19% of Victorians who identified as Aboriginal and/or Torres Strait Islander reside in the NEPHU catchment.

- The proportion of people living in the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander is lower than for Victoria overall (n = 65,639, 1.0% of the state population).

- The majority of people living in the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander reside in the LGAs of Whittlesea (n = 2,270), Hume (n = 1,870), Yarra Ranges (n = 1,713), Darebin (n = 1,441), and Knox (n = 1,022).

- Despite having a smaller number of residents who identified as Aboriginal and/or Torres Strait Islander, these residents are concentrated in Darebin (27 people per square km) and Yarra (26 people per square km) LGAs.

- The NEPHU catchment SA2s with the largest number of residents identifying as Aboriginal and/or Torres Strait Islander are Healesville - Yarra Glen (n = 373), Lilydale - Coldstream (n = 260), and Reservoir - North East (n = 248).

- Despite having a smaller number of residents who identified as Aboriginal and/or Torres Strait Islander, these residents are concentrated in the SA2s of Collingwood (55 people per square km), Reservoir - North East (52 people per square km), Reservoir - South East (44 people per square km), and Fitzroy (41 people per square km).
:::

\newpage

```{r}
# Figure 4A-1
f_caption_figure("Number of people who identified as Aboriginal and/or Torres Strait Islander, Victoria, by LPHU, 2021")

population_lphu %>% 
  dplyr::filter(lphu_name != "VIC") %>% 
  #
  ggplot() +
  #
  geom_col(aes(x = forcats::fct_reorder(lphu_name, desc(aboriginal_n)), y = aboriginal_n),
           col  = colour_black,
           fill = colour_lightblue) +
  #
  geom_text(aes(x = forcats::fct_reorder(lphu_name, desc(aboriginal_n)), y = aboriginal_n, label = format(aboriginal_n, big.mark = ",")),
            col     = colour_white,
            size    = 3,
            nudge_y = -350) +
  #
  scale_x_discrete(name   = "", 
                   labels = c("NEPHU" = expression(bold(NEPHU)), 
                              parse   = TRUE)) +
  #
  scale_y_continuous(limits = c(0, NA),
                     breaks = scales::breaks_width(1500),
                     expand = expansion(add = c(0, 250)),
                     labels = scales::comma_format(big.mark = ",")) +
  #
  labs(x = NULL,
       y = "Number of people") +
  #
  theme_classic() +
  #
  theme(axis.title   = element_text(size = 9),
        axis.title.y = element_text(margin = margin(0, 10, 0, 0)),
        plot.margin  = margin(5, 5, 0, 5))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

```{r}
# Table 4A-1
f_caption_table("Number and percentage of LPHU catchment population who identified as Aboriginal and/or Torres Strait Islander, Victoria, by LPHU, 2021")

population_lphu %>%
  dplyr::mutate(aboriginal_prop          = round(aboriginal_prop, digits = 1),
                aboriginal_prop_per_lphu = round(aboriginal_prop_per_lphu, digits = 1)) %>% 
  #
  dplyr::select(lphu_name,
                aboriginal_n,
                aboriginal_prop,
                aboriginal_prop_per_lphu) %>% 
  #
  f_table_population(total_row     = 10,
                     table_headers = c("LPHU",
                                       "Number of Aboriginal\nand/or Torres Strait\nIslander people",
                                       "% of total LPHU\npopulation",
                                       "% of Victorian Aboriginal\nand/or Torres Strait\nIslander population"))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

\newpage

```{r}
# Figure 4A-2
f_caption_figure("Number of people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by LGA, 2021")

population_lga %>% 
  dplyr::filter(lga_name != "NEPHU") %>% 
  #
  ggplot() +
  #
  geom_col(aes(x = forcats::fct_reorder(lga_name, desc(aboriginal_n)), y = aboriginal_n),
           col  = colour_black,
           fill = colour_lightblue) +
  #
  geom_text(aes(x = forcats::fct_reorder(lga_name, desc(aboriginal_n)), y = aboriginal_n, label = format(aboriginal_n, big.mark = ",")),
            col     = colour_white,
            size    = 3,
            nudge_y = -100) +
  #
  scale_x_discrete(guide  = guide_axis(angle = 90)) +
  #
  scale_y_continuous(limits = c(0, NA),
                     breaks = scales::breaks_width(250),
                     expand = expansion(add = c(0, 50)),
                     labels = scales::comma_format(big.mark = ",")) +
  #
  labs(x = NULL,
       y = "Number of people") +
  #
  theme_classic() +
  #
  theme(axis.title   = element_text(size = 9),
        axis.title.y = element_text(margin = margin(0, 10, 0, 0)),
        plot.margin  = margin(5, 5, 5, 5))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

```{r}
# Table 4A-2
f_caption_table("Number and percentage of people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by LGA, 2021")

population_lga %>%
  dplyr::mutate(aboriginal_prop         = round(aboriginal_prop, digits = 1),
                aboriginal_prop_per_lga = round(aboriginal_prop_per_lga, digits = 1)) %>% 
  #
  dplyr::select(lga_name,
                aboriginal_n,
                aboriginal_prop,
                aboriginal_prop_per_lga) %>% 
  #
  f_table_population(total_row     = 13,
                     table_headers = c("LGA",
                                       "Number of Aboriginal and/or Torres Strait Islander people",
                                       "% of total LGA population",
                                       "% of NEPHU Aboriginal and/or Torres Strait Islander people"))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

\newpage

```{r}
# Figure 4A-3
f_caption_figure("Population density for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by LGA, 2021")

ggplot(density_lga) +
  geom_sf(aes(fill = pop_dens), 
          col       = colour_black, 
          linewidth = 0.25) +
  #
  scale_fill_gradientn(colours = c(colour_gradient_low, colour_gradient_mid, colour_gradient_high),
                       name    = "Population density for people who identified as\nAboriginal and/or Torres Strait Islander") +
  #
  geom_sf(data = nephu_lga.sf, 
          #
          col       = colour_black,  
          fill      = NA, 
          linewidth = 1) +
  #
  geom_sf_text(data = density_lga %>% 
                 filter(!(lga_name %in% nudge_lga)), 
               aes(label = pop_dens_label), 
               size = 2) + 
  #
  geom_sf_text(data = density_lga %>% 
                 filter(lga_name == "Darebin"),
               aes(label = pop_dens_label), 
               size = 2,
               nudge_x = -0.07, nudge_y = -0.01) +
  #
  geom_sf_text(data = density_lga %>% 
                 filter(lga_name == "Yarra"),
               aes(label = pop_dens_label), 
               size = 2,
               nudge_x = -0.04, nudge_y = -0.01) +
  #
  geom_sf_text(data = density_lga %>% 
                 filter(lga_name == "Boroondara"),
               aes(label = pop_dens_label),
               size = 2,
               nudge_x = -0.07, nudge_y = -0.04) +
  #
  geom_sf_text(data = density_lga %>% 
                 filter(lga_name == "Maroondah"),
               aes(label = pop_dens_label),
               size = 2,
               nudge_x = 0.04, nudge_y = 0.01) +
  #
  geom_sf_text(data = density_lga %>% 
                 filter(lga_name == "Banyule"),
               aes(label = pop_dens_label),
               size = 2,
               nudge_x = 0.02, nudge_y = 0.02) +
  #
  theme_void() +
  #
  theme(legend.position = "bottom",
        legend.title    = element_text(size = 10))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

```{r}
# Figure 4A-4
f_caption_figure("Population density for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by SA2, 2021")

ggplot(density_sa2) +
  geom_sf(aes(fill = pop_dens), 
          col       = colour_black, 
          linewidth = 0.25) +
  #
  scale_fill_gradientn(colours = c(colour_gradient_low, colour_gradient_mid, colour_gradient_high),
                       name    = "Population density for people who identified as\nAboriginal and/or Torres Strait Islander") +
  #
  geom_sf(data = nephu_lga.sf,
          #
          col       = colour_black,  
          fill      = NA, 
          linewidth = 1) +
  #
  theme_void() +
  #
  theme(legend.position = "bottom",
        legend.title    = element_text(size = 10))
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

\newpage

```{r}
# Table 4A-3
f_caption_table("SA2s with at least 200 residents who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, 2021")

population_sa2 %>%
  dplyr::mutate(aboriginal_prop         = round(aboriginal_prop, digits = 1),
                aboriginal_prop_per_sa2 = round(aboriginal_prop_per_sa2, digits = 1)) %>% 
  #
  dplyr::filter(aboriginal_n >= 200 & sa2_code_2021 != "NEPHU") %>% 
  #
  dplyr::select(sa2_name,
                aboriginal_n,
                aboriginal_prop,
                aboriginal_prop_per_sa2) %>% 
  #
  dplyr::arrange(desc(aboriginal_n)) %>% 
  #
  f_table_population(total_row     = NULL,
                     table_headers = c("SA2",
                                       "Number of Aboriginal and/or Torres Strait Islander people",
                                       "% of total SA2\npopulation",
                                       "% of total NEPHU Aboriginal and/or Torres Strait Islander people")) %>% 
  #
  flextable::bold(bold = FALSE,
                  part = "body") %>% 
  #
  flextable::width(j = 1,
                   width = 2.5) %>%
  #
  flextable::width(j = 2:4,
                   width = 1.5)
```

#### Data notes:

::: {custom-style="Footnotes"}
- Data are obtained from the [ABS Census 2021](https://www.abs.gov.au/census) and are publicly available at Local Government Area (LGA), ABS Statistical Area Level 2 (SA2), and Indigenous Area of Residence (IARE) level.

- Aboriginal and/or Torres Strait Islander peoples are defined as those who identified themselves as Aboriginal and/or Torres Strait Islander in the ABS Census 2021.

- Reported counts and percentages are a likely underestimate due to under-identification.
:::

