---
title: "NEPHU First Nations Population Profile"
subtitle: "Demographics: Gender Diversity"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "05B Demographics Gender Diversity ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
# 
source(here::here("Code", "00_Setup.R"))
```


```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 5B-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 5B-"))
  
  return(caption)
  
}
```

### What is the size and distribution of the Aboriginal and/or Torres Strait Islander gender diverse community living within the NEPHU catchment?

Data are unable to be reported at this time as Aboriginal and/or Torres Strait Islander status is not included in the publicly available Victorian Population Health Survey data.

#### Data notes:

::: {custom-style="Footnotes"}
- Data are sourced from the [Victorian Population Health Survey 2023](https://www.health.vic.gov.au/population-health-systems/victorian-population-health-survey) and report the proportion of people who identified as part of the lesbian, gay, bisexual, transgender, intersex, and queer (LGBTIQ+) community.

- This indicator is unable to be reported on at this time as Aboriginal and/or Torres Strait Islander status is not included in the publicly available Victorian Population Health Survey data.
:::

