---
title: "NEPHU First Nations Population Profile"
subtitle: "Other Determinants of Health: Child Protection"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "08B Other Child Protection ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
#
source(here::here("Code", "00_Setup.R"))

source(here::here("Code", "Functions", "Graphs", "f_graph_line_comparison.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_ctg_target.R"))

source(here::here("Code", "Functions", "Tables", "f_table_rate_year.R"))
```


```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 8B-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 8B-"))
  
  return(caption)
  
}
```

### What external factors may influence how Aboriginal and/or Torres Strait Islander people and families in the NEPHU catchment are supported to prioritise health and wellbeing, particularly in connection to caring for children and keeping families strong?

# Child Protection

::: {custom-style="Dotpt"}
This indicator aligns with Closing the Gap Target 12: By 2031, reduce the rate of over-representation of Aboriginal and Torres Strait Islander children (0–17 years old) in out-of-home care by 45% (compared to the baseline year of 2018-19).
:::

<br>

```{r}
# ------------------------------------------------------------------------------
# Child protection: out-of-home care
# Data from AIHW Child Protection National Minimum Dataset
# ------------------------------------------------------------------------------
# Read in AIHW data
protection_home <- readxl::read_excel(file.path(root_folder, subfolder_protection, "Child_Protection_National_Minimum_Dataset.xlsx"),
                                      skip  = 2,
                                      sheet = "T3") %>%
  janitor::clean_names() %>%
  #
  dplyr::mutate(
    indigenous_status = dplyr::case_when(
      row_number() %in% 58:62 ~ "aboriginal",
      row_number() %in% 64:68 ~ "non_aboriginal",
      TRUE ~ NA_character_)) %>% 
  #
  dplyr::filter(!is.na(indigenous_status))

# Data wrangling
protection_home <- protection_home %>%
  dplyr::select(year,
                indigenous_status,
                rate = vic) %>%
  #
  dplyr::mutate(
    ctg_target = dplyr::case_when(
      indigenous_status == "non_aboriginal" ~ NA_real_,
      TRUE ~ protection_home$vic[1] * 0.55),
    #
    ctg_change = dplyr::case_when(
      indigenous_status == "non_aboriginal" ~ NA_character_,
      rate >= protection_home$vic[1] * 1.1 ~ "a worsening",
      rate <  protection_home$vic[1] * 0.9 ~ "an improvement",
      TRUE ~ "no change"))

# ------------------------------------------------------------------------------
# Child protection: relationship with caregiver
# Data from AIHW Child Protection National Minimum Dataset
# ------------------------------------------------------------------------------
# Read in AIHW data
protection_relationship <- readxl::read_excel(file.path(root_folder, subfolder_ctg, "CTG12_Child_Protection_Data_Tables.xlsx"),
                                              skip  = 1,
                                              sheet = "Table SE12e.1") %>%
  janitor::clean_names() %>%
  #
  dplyr::rename(type = x2,
                year = x3,
                relationship = x5) %>%
  #
  tidyr::fill(type, year) %>% 
  #
  dplyr::filter(!is.na(vic))

# Data wrangling
protection_relationship <- protection_relationship %>%
  dplyr::select(type,
                year,
                relationship,
                value = vic) %>%
  #
  dplyr::mutate(value = as.numeric(value),
                #
                type = dplyr::case_when(
                  type == "Proportion of children" ~ "proportion",
                  type == "Number of children"     ~ "number",
                  TRUE ~ NA_character_),
                #
                relationship = dplyr::case_when(
                  relationship == "Aboriginal and Torres Strait Islander relatives/kin" ~ "First Nations relatives/kin",
                  relationship == "Other Aboriginal and Torres Strait Islander carers"  ~ "Other First Nations carers",
                  relationship == "Non-Indigenous relatives/kin"                        ~ "Non-Indigenous relatives/kin",
                  relationship == "Other non-Indigenous carers"                         ~ "Other care arrangements",
                  relationship == "Residential care or family group home"               ~ "Other care arrangements",
                  relationship == "Independent living/living arrangements unknown"      ~ "Other care arrangements",
                  TRUE ~ NA_character_)) %>% 
  #
  dplyr::filter(!is.na(relationship)) %>% 
  #
  dplyr::group_by(type, year, relationship) %>% 
  dplyr::summarise(value = sum(value)) %>% 
  dplyr::ungroup()

protection_relationship <- protection_relationship %>% 
  tidyr::pivot_wider(names_from  = "type",
                     values_from = "value") %>% 
  #
  janitor::clean_names() %>% 
  #
  dplyr::mutate(relationship = factor(relationship,
                                      levels = c("First Nations relatives/kin",
                                                 "Other First Nations carers",
                                                 "Non-Indigenous relatives/kin",
                                                 "Other care arrangements")))
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the AIHW Child Protection National Minimum Dataset.

- The out-of-home care rate for Aboriginal and/or Torres Strait Islander children in Victoria on June 30th 2023 was 103 per 1,000 population. This compares to 4.6 per 1,000 for non-Indigenous children.

- This rate shows a worsening compared to the 2019 baseline rate.

- On June 30th 2024, 82% (n = 2,365) of Aboriginal and/or Torres Strait Islander children in Victoria who were in out-of-home care had been placed with Aboriginal and/or Torres Strait Islander relatives or kin, non-Indigenous relatives or kin, or other Aboriginal and/or Torres Strait Islander carers.
:::

\newpage

```{r}
# Figure 8B-1
f_caption_figure("Out-of-home care rate (per 1,000 population) on June 30th for children aged 0-17 years, Victoria, by Aboriginal and/or Torres Strait Islander status and year")

protection_home %>% 
  f_graph_line_comparison(y_variable = rate,
                          y_max      = NA,
                          y_breaks   = 10,
                          y_expand   = 10,
                          y_title    = "Out-of-home care rate (per 1,000 population)") %>% 
  #
  f_graph_ctg_target(ctg_target = 49)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_child_protection)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_ctg_target)`

- The out-of-home care rate is calculated as the total number of children in out-of-home care per 1,000 population on June 30th of each year as estimated by the [ABS Estimated Residential Population (ERP)](https://www.abs.gov.au/statistics/people/population/population-projections-australia/2022-base-2071) for the year. ERP calculations take into account the known under-reporting of Aboriginal and/or Torres Strait Islander status in the Census. 
:::

```{r}
# Table 8B-1
f_caption_table("Out-of-home care rate (per 1,000 population) on June 30th for children aged 0-17 years, Victoria, by Aboriginal and/or Torres Strait Islander status and year")

protection_home %>% 
  dplyr::select(year,
                indigenous_status,
                rate) %>% 
  #
  dplyr::mutate(rate = round(rate, digits = 1)) %>% 
  #
  tidyr::pivot_wider(names_from  = indigenous_status,
                     values_from = rate) %>% 
  #
  f_table_rate_year() %>% 
  #
  flextable::set_header_labels(values = c("Year", "Yes\n(rate per 1,000)", "No\n(rate per 1,000)"))
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_child_protection)`

`r knitr::asis_output(note_caveat_underidentification)`

- The out-of-home care rate is calculated as the total number of children in out-of-home care per 1,000 population on June 30th of each year as estimated by the [ABS Estimated Residential Population (ERP)](https://www.abs.gov.au/statistics/people/population/population-projections-australia/2022-base-2071) for the year. ERP calculations take into account the known under-reporting of Aboriginal and/or Torres Strait Islander status in the Census. 
:::

\newpage

```{r}
# Figure 8B-2
f_caption_figure("Relationship to carer for Aboriginal and/or Torres Strait Islander children in out-of-home care, Victoria, 2019-2024")

ggplot(protection_relationship) +
  geom_col(aes(x = year, y = number, fill = forcats::fct_rev(relationship)),
           col = colour_gray) +
  #
  scale_y_continuous(limits = c(0, NA),
                     breaks = scales::breaks_width(500),
                     expand = expansion(add = c(0, 250))) +
  #
  scale_fill_manual(values = c(colour_yellow, colour_orange, colour_green, colour_lightblue),
                    labels = c("Other care\narrangements", 
                               "Non-Indigenous\nrelatives/kin", 
                               "Other First\nNations carers", 
                               "First Nations\nrelatives/kin"),
                    name   = NULL) +
  #
  labs(x = NULL,
       y = "Number of children") +
  #
  theme_classic() +
  #
  theme(plot.margin = margin(5, 5, 5, 5),
        #
        legend.title       = element_text(size = 9),
        legend.location    = "plot",
        legend.position    = "bottom",
        legend.box.spacing = unit(5, "pt"),
        legend.margin      = margin(c(0, 0, 0, 0)),
        #
        axis.title   = element_text(size = 9),
        axis.title.y = element_text(margin = margin(0, 10, 0, 0))) +
  #
  guides(fill = guide_legend(reverse = TRUE))
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_child_protection)`

`r knitr::asis_output(note_caveat_underidentification)`

- 'Other care arrangements' includes children in out-of-home care who were living with non-Indigenous carers who were not relatives/kin, living in residential care or family group homes, living independently, and where the living arrangements were not known.
:::

```{r}
# Table 8B-2
f_caption_table("Relationship to carer for Aboriginal and/or Torres Strait Islander children in out-of-home care, Victoria, 2019-2024")

protection_relationship %>%
  tidyr::pivot_wider(names_from  = "relationship",
                     values_from = c("number", "proportion"),
                     names_vary  = "slowest") %>% 
  #
  janitor::clean_names() %>% 
  #
  dplyr::select(year,
                ends_with("first_nations_relatives_kin"),
                ends_with("other_first_nations_carers"),
                ends_with("non_indigenous_relatives_kin"),
                ends_with("other_care_arrangements")) %>% 
  #
  flextable::flextable() %>%
  #
  flextable::set_header_labels(values = c("Year", 
                                          "n", "%", 
                                          "n", "%",
                                          "n", "%", 
                                          "n", "%")) %>%
  #
  flextable::add_header_row(values    = c(" ", 
                                          "First Nations\nrelatives/kin",
                                          "Other First\nNations carers",
                                          "Non-Indigenous\nrelatives/kin",
                                          "Other care\narrangements"),
                            colwidths = c(1, 2, 2, 2, 2)) %>%
  #
  flextable::align(i = 1,
                   align = "center",
                   part  = "header") %>%
  #
  flextable::align(j = 1,
                   align = "left",
                   part  = "body") %>%
  #
  flextable::align(j = c(2:9),
                   align = "right",
                   part  = "all") %>%
  #
  flextable::align(i = 1,
                   align = "center",
                   part  = "header") %>%
  #
  flextable::fontsize(size = 10,
                      part = "all") %>% 
  #
  flextable::bold(part = "header") %>%
  #
  flextable::line_spacing(space = 0.75,
                          part  = "body")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_child_protection)`

`r knitr::asis_output(note_caveat_underidentification)`

- 'Other care arrangements' includes children in out-of-home care who were living with non-Indigenous carers who were not relatives/kin, living in residential care or family group homes, living independently, and where the living arrangements were not known.
:::

