---
title: "NEPHU First Nations Population Profile"
subtitle: "Other Determinants of Health: Family Violence"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "08C Other Family Violence ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
#
source(here::here("Code", "00_Setup.R"))
```

**Table of Contents**

```{r}
#
block_toc(level = 2)
```

\newpage

```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 8C-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 8C-"))
  
  return(caption)
  
}
```

### What external factors may influence how Aboriginal and/or Torres Strait Islander people and families in the NEPHU catchment are supported to prioritise health and wellbeing, particularly in connection to caring for children and keeping families strong?

# Women Experiencing Domestic Physical or Threatened Harm

::: {custom-style="Dotpt"}
This indicator aligns with Closing the Gap Target 13: By 2031, the rate of all forms of family violence and abuse against Aboriginal and Torres Strait Islander women and children is reduced at least by 50% (compared to the baseline year of 2018-19).
:::

<br>

```{r}
# ------------------------------------------------------------------------------
# Family violence: women experiencing domestic physical or threatened harm
# Data from ABS Aboriginal and Torres Strait Islander Health Survey (2018-29)
# ------------------------------------------------------------------------------
# Read in ABS data
violence_women <- readxl::read_excel(file.path(root_folder, subfolder_ctg, "CTG13_Family_Safety_Data_Tables.xlsx"),
                                     skip  = 1,
                                     sheet = "Table CtG13A.1") %>%
  janitor::clean_names() %>%
  #
  dplyr::rename(violence = x6) %>%
  #
  dplyr::filter(!is.na(vic) & vic != "..")

# Data wrangling
violence_women <- violence_women %>%
  dplyr::select(violence,
                value = vic,
                unit) %>%
  #
  dplyr::mutate(value = as.numeric(value),
                #
                violence = dplyr::case_when(
                  violence == "Experienced domestic physical or face-to-face threatened physical harm (b)"        ~ "Yes",
                  violence == "Did not experience domestic physical or face-to-face threatened physical harm (b)" ~ "No",
                  #
                  violence == "Total (c)" ~ "Total",
                  TRUE ~ NA_character_))
```

::: {custom-style="Dotpt"}
- Data are obtained from the 2018-19 ABS National Aboriginal and Torres Strait Islander Health Survey and are only available at a statewide level.

- During 2018-2019, 7.5% of Aboriginal and/or Torres Strait Islander female survey respondents aged 15 years or over living in Victoria reported that they have experienced domestic physical or face-to-face threatened physical harm in the 12 months prior to the survey.

- More recent data are not available, as this indicator was not included in the 2022-2023 National Aboriginal and/or Torres Strait Islander Health Survey.
:::

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_natsihs_2019)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_survey_estimate)`

`r knitr::asis_output(note_caveat_unknown_survey)`
:::

\newpage

# Reported Family Violence Incidents

```{r}
# ------------------------------------------------------------------------------
# Family violence: reported incidents
# Data from Crime Statistics Agency
# ------------------------------------------------------------------------------
# Read in Crime Statistics Agency data
violence_incidents <- readxl::read_excel(file.path(root_folder, subfolder_crime, "Indigenous_Data_Tables_Family_Incidents_Visualisation_Year_Ending_December_2023.xlsx"),
                                         sheet = "Table 01") %>%
  janitor::clean_names()

# Data wrangling
violence_incidents <- violence_incidents %>%
  dplyr::filter(afm_age_group == "Total",
                afm_indigenous_status != "Total People") %>% 
  #
  dplyr::select(year,
                sex = afm_sex,
                indigenous_status = afm_indigenous_status,
                n = afm_counter) %>%
  #
  dplyr::mutate(n = as.numeric(n),
                #
                sex = dplyr::case_when(
                  sex == "Males"   ~ "Male",
                  sex == "Females" ~ "Female",
                  sex == "People"  ~ "Total",
                  TRUE ~ NA_character_),
                #
                indigenous_status = dplyr::case_when(
                  indigenous_status == "Aboriginal and/or Torres Strait Islander" ~ "Yes",
                  indigenous_status == "Non-Indigenous" ~ "No",
                  TRUE ~ NA_character_))
```

::: {custom-style="Dotpt"}
- Data are obtained from the Victorian Crime Statistics Agency and are only available at a statewide level.

- The number of family violence incidents reported by affected Aboriginal and/or Torres Strait Islander family members living in Victoria increased from 4,696 in 2019 to 5,687 in 2023.

- Family violence incidents were more commonly reported by females than by males.

- The number of family violence incidents reported increased each year for both males and females.
:::

```{r}
# Figure 8C-1
f_caption_figure("Number of family violence incidents reported by affected Aboriginal and/or Torres Strait Islander family members, Victoria, by sex and year, 2019-2023")

violence_incidents %>% 
  dplyr::filter(sex != "Total" & indigenous_status == "Yes") %>% 
  #
  ggplot() +
  #
  geom_line(aes(x = year, y = n, group = sex, col = sex),
            linewidth = 1.5) +
  #
  scale_y_continuous(limits = c(0, NA),
                     breaks = scales::breaks_width(500),
                     expand = expansion(add = c(0, 250)),
                     labels = scales::comma_format(big.mark = ",")) +
  #
  scale_color_manual(values = c(colour_lightblue, colour_dodgerblue),
                     labels = c("Female", "Male"),
                     name   = NULL) +
  #
  labs(x = NULL,
       y = "Number of reported incidents") +
  #
  theme_classic() +
  #
  theme(plot.margin = margin(5, 5, 5, 5),
        #
        legend.title       = element_text(size = 9),
        legend.position    = "bottom",
        legend.location    = "plot",
        legend.box.spacing = unit(10, "pt"),
        legend.margin      = margin(c(0, 10, 0, 0)),
        #
        axis.title   = element_text(size = 9),
        axis.title.y = element_text(margin = margin(0, 10, 0, 0)))
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_crime)`

`r knitr::asis_output(note_caveat_underidentification)`

- 'Family violence incidents' are defined as those where a Victoria Police Risk Assessment and Risk Management Report (also known as an L17 form) was completed and recorded on LEAP.

- An ‘affected family member’ is the individual who is deemed to be affected by events occurring during a family incident.

    - The other individual involved in a family incident is referred to as the ‘other party’.
    
    - The other party could be a current partner, former partner, or a family member.
:::

\newpage

```{r}
# Table 8C-1
f_caption_table("Number of family violence incidents reported by affected Aboriginal and/or Torres Strait Islander family members, Victoria, by sex and year, 2019-2023")

violence_incidents %>% 
  dplyr::filter(indigenous_status == "Yes") %>% 
  #
  dplyr::select(-indigenous_status) %>% 
  #
  tidyr::pivot_wider(names_from  = sex,
                     values_from = n) %>% 
  #
  dplyr::arrange(year) %>% 
  #
  dplyr::mutate(year = as.character(year)) %>% 
  #
  flextable::flextable() %>%
  #
  flextable::set_header_labels(values = c("Year", "Female", "Male", "Total")) %>% 
  #
  flextable::align(j = 1,
                   align = "left",
                   part  = "all") %>%
  #
  flextable::align(j = c(2:4),
                   align = "right",
                   part  = "all") %>%
  #
  flextable::fontsize(size = 10,
                      part = "all") %>%
  #
  flextable::bold(part = "header") %>%
  #
  flextable::width(j = 1:4,
                   width = 1) %>%
  #
  flextable::line_spacing(space = 0.75,
                          part  = "body")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_crime)`

`r knitr::asis_output(note_caveat_underidentification)`

- 'Family violence incidents' are defined as those where a Victoria Police Risk Assessment and Risk Management Report (also known as an L17 form) was completed and recorded on LEAP.

- An ‘affected family member’ is the individual who is deemed to be affected by events occurring during a family incident.

    - The other individual involved in a family incident is referred to as the ‘other party’.
    
    - The other party could be a current partner, former partner, or a family member.
:::

