---
title: "NEPHU First Nations Population Profile"
subtitle: "Health Consequences: Asthma and Allergies"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "10D Consequences Asthma ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
#
source(here::here("Code", "00_Setup.R"))

source(here::here("Code", "Functions", "Data prep", "f_read_census_lga.R"))
source(here::here("Code", "Functions", "Data prep", "f_wrangle_census_lga.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_census_agesex.R"))
source(here::here("Code", "Functions", "Data prep", "f_wrangle_census_agesex.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_natsihs_sex.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_natsihs_sex_vic.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_phidu_iare_hospital.R"))

source(here::here("Code", "Functions", "Graphs", "f_graph_lga.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_agesex.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_expected.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_iare.R"))

source(here::here("Code", "Functions", "Tables", "f_table_expected.R"))
source(here::here("Code", "Functions", "Tables", "f_table_survey_sex.R"))
source(here::here("Code", "Functions", "Tables", "f_table_iare.R"))
```

**Table of Contents**

```{r}
#
block_toc(level = 2)
```

\newpage

```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 10D-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 10D-"))
  
  return(caption)
  
}
```

### What chronic conditions affect Aboriginal and/or Torres Strait Islander people living in the NEPHU catchment?

# Asthma 

## Prevalence

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Asthma, by LGA
# Data from ABS Census using TableBuilderPro
# ------------------------------------------------------------------------------
# Read in Census data
health_asthma_lga <- f_read_census_lga("Aboriginal_Health_Asthma_LGA.csv",
                                       variable = "asthma") %>% 
  #
  dplyr::filter(asthma != "Not stated")

# Data wrangling
health_asthma_lga <- health_asthma_lga %>%
  #
  dplyr::mutate(asthma = dplyr::case_when(
    asthma == "Has asthma" ~ "yes",
    TRUE ~ "no")) %>% 
  #
  f_wrangle_census_lga(variable = asthma,
                       level    = "person",
                       dichot   = "yes")

# ------------------------------------------------------------------------------
# Asthma, by age and sex
# Data from ABS Census using TableBuilderPro
# ------------------------------------------------------------------------------
# Read in Census data
health_asthma_agesex <- f_read_census_agesex("Aboriginal_Health_Asthma_AgeSex.csv",
                                             variable = "asthma") %>% 
  #
  dplyr::filter(asthma != "Not stated")

# Data wrangling
health_asthma_agesex <- health_asthma_agesex %>% 
  #
  dplyr::mutate(asthma = dplyr::case_when(
    asthma == "Has asthma" ~ "yes",
    TRUE ~ "no")) %>%  
  #
  f_wrangle_census_agesex(variable = asthma,
                          dichot   = "yes")
```


```{r}
#
results <- list()
data    <- health_asthma_lga

results$rank_n <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_n)) %>% 
  dplyr::select(lga_name,
                aboriginal_n)

results$rank_prop <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_prop)) %>% 
  dplyr::select(lga_name,
                aboriginal_prop)

results$rank_diff <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_difference)) %>% 
  dplyr::select(lga_name,
                aboriginal_difference)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the ABS Census 2021.

- Overall, 17% (n = 1,902) of people living in the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census have been told by a doctor or nurse that they have asthma. This is higher than for non-Indigenous people living in the NEPHU catchment (8.5%).

- The number of people living in different LGAs within the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census who have been told by a doctor or nurse that they have asthma ranged from 388 (Whittlesea LGA) to 25 (Manningham LGA).

- The gap between Aboriginal and/or Torres Strait Islander and non-Indigenous people was biggest for Whittlesea and Hume LGAs.

- The percentage of people living in different LGAs within the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census who have been told by a doctor or nurse that they have asthma ranged from 18% (Maroondah, Whittlesea, and Hume LGAs) to 8.8% (Manningham LGA).

- The number of people who have been told by a doctor or nurse that they have asthma was highest for people aged 20-29 years for both males and females.
:::

\newpage

```{r}
# Figure 10D-1
f_caption_figure("(A) Number and (B) percentage of people who identified as Aboriginal and/or Torres Strait Islander and who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by LGA, 2021")

figure_number <- health_asthma_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_lga(y_variable = aboriginal_n,
              y_max      = NA,
              y_breaks   = 50,
              y_expand   = 20,
              y_title    = "Number of people",
              plot_tag   = "A")

figure_percent <- health_asthma_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_lga(y_variable = aboriginal_prop,
              y_max      = 25,
              y_breaks   = 5,
              y_expand   = 0.5,
              y_title    = "Percentage of people",
              plot_tag   = "B")

figure_number + figure_percent
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

```{r}
# Figure 10D-2
f_caption_figure("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by LGA, 2021")

health_asthma_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_expected(variable = lga_name,
                   y_breaks = 50,
                   y_expand = 20)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

\newpage

```{r}
# Table 10D-1
f_caption_table("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by LGA, 2021")

health_asthma_lga %>% 
  dplyr::filter(lga_name %in% c(nephu_lga, "NEPHU")) %>%
  #
  f_table_expected(variable       = lga_name,
                   variable_label = "LGA",
                   group_label    = " ",
                   total_row      = 13)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

\newpage

```{r}
# Figure 10D-3
f_caption_figure("(A) Number and (B) percentage of people who identified as Aboriginal and/or Torres Strait Islander and who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by age and sex, 2021")

figure_female_number <- health_asthma_agesex %>%
  f_graph_agesex(sex        = "Female",
                 y_variable = aboriginal_n,
                 y_max      = 220,
                 y_breaks   = 20,
                 y_expand   = 3,
                 y_title    = "Number of females",
                 plot_title = "Females",
                 plot_tag   = "A")

figure_female_percent <- health_asthma_agesex %>%
  f_graph_agesex(sex        = "Female",
                 y_variable = aboriginal_prop,
                 y_max      = 50,
                 y_breaks   = 5,
                 y_expand   = 0.5,
                 y_title    = "Percentage of females",
                 plot_title = " ",
                 plot_tag   = "B")

figure_male_number <- health_asthma_agesex %>%
  f_graph_agesex(sex        = "Male",
                 y_variable = aboriginal_n,
                 y_max      = 220,
                 y_breaks   = 20,
                 y_expand   = 3,
                 y_title    = "Number of males",
                 plot_title = "Males",
                 plot_tag   = "A")

figure_male_percent <- health_asthma_agesex %>%
  f_graph_agesex(sex        = "Male",
                 y_variable = aboriginal_prop,
                 y_max      = 50,
                 y_breaks   = 5,
                 y_expand   = 0.5,
                 y_title    = "Percentage of males",
                 plot_title = " ",
                 plot_tag   = "B")

figure_female_number + figure_female_percent
figure_male_number + figure_male_percent
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

```{r} 
# Figure 10D-4
f_caption_figure("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by age and sex, 2021") 

health_asthma_agesex %>%  
  dplyr::filter(age_group %in% age_group_lvl) %>%  
  # 
  dplyr::mutate(age_group = factor(age_group, levels = age_group_lvl)) %>% 
  #
  f_graph_expected(variable = age_group, 
                   y_breaks = 20, 
                   y_expand = 10) +
  #
  facet_wrap(~sex,
             axes = "all")
``` 

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

```{r} 
# Table 10D-2
f_caption_table("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have asthma, NEPHU catchment, by age and sex, 2021") 

health_asthma_agesex %>% 
  dplyr::filter(sex == "Female") %>%  
  # 
  f_table_expected(variable       = age_group,
                   variable_label = "Age group",
                   group_label    = "Females",
                   total_row      = 12)
  
health_asthma_agesex %>% 
  dplyr::filter(sex == "Male") %>%  
  # 
  f_table_expected(variable       = age_group,
                   variable_label = "Age group",
                   group_label    = "Males",
                   total_row      = 12)
``` 

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

## Hospital Admissions

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Hospitalisations - asthma
# Data from PHIDU Social Health Atlas
# ------------------------------------------------------------------------------
# Read in PHIDU data
hospital_asthma <- f_read_phidu_iare_hospital(data_sheet    = "Admissions_principal_diag",
                                              column_select = "admissions_for_asthma_aboriginal_people")

# Data wrangling
hospital_asthma <- hospital_asthma %>% 
  dplyr::mutate(iare_name = factor(iare_name, levels = iare_inc_vic_lvl),
                #
                hospital_n_label = round(hospital_n, digits = 0),
                #
                hospital_n_label = dplyr::case_when(
                  is.na(hospital_n) ~ "*",
                  TRUE ~ format(hospital_n_label, big.mark = ",")),
                #
                hospital_rate_label = round(hospital_rate, digits = 0),
                #
                hospital_rate_label = dplyr::case_when(
                  is.na(hospital_rate) ~ "*",
                  TRUE ~ format(hospital_rate_label, big.mark = ",")),
                #
                hospital_ratio_label = round(hospital_ratio, digits = 1),
                #
                hospital_ratio_label = dplyr::case_when(
                  is.na(hospital_ratio) ~ "*",
                  TRUE ~ format(hospital_ratio_label, big.mark = ","))) %>% 
  #
  dplyr::select(iare_name,
                iare_name_short,
                starts_with("hospital")) %>% 
  #
  dplyr::arrange(iare_name)
```


```{r}
#
results <- list()

data <- hospital_asthma %>% 
  dplyr::rename(n     = hospital_n,
                rate  = hospital_rate,
                ratio = hospital_ratio)

results$rank_n <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::select(iare_name,
                n)

results$rank_rate <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(rate)) %>% 
  dplyr::select(iare_name,
                rate)

results$rank_ratio <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(ratio)) %>% 
  dplyr::select(iare_name,
                ratio)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the PHIDU Social Health Atlas, compiled from the Victorian Admitted Episodes Dataset.

- During the four-year period 01 July 2017 to 30 June 2021 there were 292 hospital admissions for asthma for Aboriginal and/or Torres Strait Islander people living in Greater Melbourne.

- The number of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 51 (Northcote/Preston/Whittlesea IARE) to 6 (Melbourne East IARE).

- The age-standardised rate of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 287 per 100,000 population (Northcote/Preston/Whittlesea IARE) to 93 per 100,000 population (Melbourne East IARE).

- 3 of the 8 IAREs in the NEPHU catchment area with data available for reporting had an age-standardised admission rate above the average for all Aboriginal and/or Torres Strait Islander people living in Greater Melbourne (Northcote/Preston/Whittlesea, Yarra Ranges, and Moreland/Broadmeadows IAREs).
:::

\newpage

```{r}
# Figure 10D-5
f_caption_figure("(A) Number and (B) age-standardised rate (per 100,000 population) of hospital admissions for asthma for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

figure_number <- hospital_asthma %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_n,
               text_pos   = 2,
               y_label    = hospital_n_label,
               y_max      = NA,
               y_breaks   = 5,
               y_expand   = 5,
               y_title    = "Number of admissions",
               plot_tag   = "A")

figure_rate <- hospital_asthma %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_rate,
               text_pos   = 10,
               y_label    = hospital_rate_label,
               y_max      = NA,
               y_breaks   = 50,
               y_expand   = 20,
               y_title    = "Age-standardised rate",
               plot_tag   = "B")

figure_number + figure_rate
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

- Admissions for 'asthma' are defined as those with a principal diagnosis code of J45 (asthma) or J46 (status asthmaticus), coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Chronic asthmatic (obstructive) bronchitis, chronic obstructive asthma, and eosinophilic asthma are excluded.
:::

\newpage

```{r}
# Table 10D-3
f_caption_table("Hospital admissions for asthma for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

hospital_asthma %>% 
  dplyr::select(iare_name,
                hospital_n_label,
                hospital_rate_label,
                hospital_ratio_label) %>%
  #
  f_table_iare(table_headers = c("Number of\nadmissions", "Age-standardised rate\n(per 100,000)", "Standardised\nratio"),
               last_column   = 4) %>% 
  #
  flextable::width(j = 3,
                   width = 1.75)
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_ratio)`

- Admissions for 'asthma' are defined as those with a principal diagnosis code of J45 (asthma) or J46 (status asthmaticus), coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Chronic asthmatic (obstructive) bronchitis, chronic obstructive asthma, and eosinophilic asthma are excluded.
:::

\newpage

# Allergic Rhinitis

## Prevalence

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Allergic rhinitis (hay fever)
# Data from ABS National Aboriginal and Torres Strait Islander Health Survey
# ------------------------------------------------------------------------------
# Read in NATSIHS data
health_allergy <- f_read_natsihs_sex("Indicator_Vic_Sex_Chronic_Conditions.csv")

# Data wrangling
health_allergy <- health_allergy %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(noallergy_n = total_n - hay_fever_and_allergic_rhinitis_n) %>% 
  dplyr::ungroup() %>% 
  #
  janitor::adorn_totals(fill = "Total") %>%
  #
  dplyr::rename(yesallergy_n = hay_fever_and_allergic_rhinitis_n,
                answered_n   = total_n) %>% 
  #
  dplyr::mutate(yesallergy_prop = yesallergy_n / answered_n * 100,
                noallergy_prop  = noallergy_n / answered_n * 100,
                answered_prop   = answered_n / answered_n * 100) %>% 
  #
  dplyr::select(sex,
                starts_with("yesallergy"),
                starts_with("noallergy"),
                starts_with("answered"))
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the 2022-23 ABS National Aboriginal and Torres Strait Islander Health Survey.

- Overall, 37% of Aboriginal and/or Torres Strait Islander survey respondents living in Greater Melbourne reported that they were living with allergic rhinitis (hay fever). This equates to approximately 14,200 Aboriginal and/or Torres Strait Islander people.

- The percentage of people living with allergic rhinitis was similar for males and females (36% vs. 37%).
:::

```{r}
# Table 10D-4
f_caption_table("Self-reported prevalence of allergic rhinitis (hay fever) for people who identified as Aboriginal and/or Torres Strait Islander, Greater Melbourne, by sex, 2022-2023")

x_labels <- c("yesallergy" = "Yes",
              "noallergy"  = "No",
              "answered"   = "Total")

health_allergy %>% 
  f_table_survey_sex(x_labels       = x_labels,
                     variable_label = "Allergic rhinitis\n(hay fever)",
                     total_row      = 3)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_natsihs)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_survey_estimate)`

`r knitr::asis_output(note_caveat_unknown_survey)`
:::

