---
title: "NEPHU First Nations Population Profile"
subtitle: "Health Consequences: Kidney Disease"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "10H Consequences Kidney Disease ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
#
source(here::here("Code", "00_Setup.R"))

source(here::here("Code", "Functions", "Data prep", "f_read_census_lga.R"))
source(here::here("Code", "Functions", "Data prep", "f_wrangle_census_lga.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_census_agesex.R"))
source(here::here("Code", "Functions", "Data prep", "f_wrangle_census_agesex.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_natsihs_sex.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_phidu_iare_hospital.R"))

source(here::here("Code", "Functions", "Graphs", "f_graph_lga.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_agesex.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_expected.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_iare.R"))

source(here::here("Code", "Functions", "Tables", "f_table_expected.R"))
source(here::here("Code", "Functions", "Tables", "f_table_survey_sex.R"))
source(here::here("Code", "Functions", "Tables", "f_table_iare.R"))
```

**Table of Contents**

```{r}
#
block_toc(level = 2)
```

\newpage

```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 10H-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 10H-"))
  
  return(caption)
  
}
```

### What chronic conditions affect Aboriginal and/or Torres Strait Islander people living in the NEPHU catchment?

# Kidney Disease

## Prevalence

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Kidney disease, by LGA
# Data from ABS Census using TableBuilderPro
# ------------------------------------------------------------------------------
# Read in Census data
health_kidney_lga <- f_read_census_lga("Aboriginal_Health_Kidney_LGA.csv",
                                       variable = "kidney") %>% 
  #
  dplyr::filter(kidney != "Not stated")

# Data wrangling
health_kidney_lga <- health_kidney_lga %>%
  #
  dplyr::mutate(kidney = dplyr::case_when(
    kidney == "Has kidney disease" ~ "yes",
    TRUE ~ "no")) %>% 
  #
  f_wrangle_census_lga(variable = kidney,
                       level    = "person",
                       dichot   = "yes")

# ------------------------------------------------------------------------------
# Kidney disease, by age and sex
# Data from ABS Census using TableBuilderPro
# ------------------------------------------------------------------------------
# Read in Census data
health_kidney_agesex <- f_read_census_agesex("Aboriginal_Health_Kidney_AgeSex.csv",
                                             variable = "kidney") %>% 
  #
  dplyr::filter(kidney != "Not stated")

# Data wrangling
health_kidney_agesex <- health_kidney_agesex %>% 
  #
  dplyr::mutate(kidney = dplyr::case_when(
    kidney == "Has kidney disease" ~ "yes",
    TRUE ~ "no")) %>%  
  #
  f_wrangle_census_agesex(variable = kidney,
                          dichot   = "yes")
```


```{r}
#
results <- list()
data    <- health_kidney_lga

results$rank_n <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_n)) %>% 
  dplyr::select(lga_name,
                aboriginal_n)

results$rank_prop <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_prop)) %>% 
  dplyr::select(lga_name,
                aboriginal_prop)

results$rank_diff <- data %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  dplyr::arrange(desc(aboriginal_difference)) %>% 
  dplyr::select(lga_name,
                aboriginal_difference)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the ABS Census 2021.

- Overall, 1.2% (n = 141) of people living in the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census have been told by a doctor or nurse that they have kidney disease. This is higher than for non-Indigenous people living in the NEPHU catchment (0.9%).

- The number of people living in different LGAs within the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census who have been told by a doctor or nurse that they have kidney disease ranged from 26 (Darebin LGA) to 0 (Manningham and Yarra LGAs).

- The gap between Aboriginal and/or Torres Strait Islander and non-Indigenous people was biggest for Darebin and Hume LGAs.

- The percentage of people living in different LGAs within the NEPHU catchment who identified as Aboriginal and/or Torres Strait Islander in the Census who have been told by a doctor or nurse that they have kidney disease ranged from 2.0% (Whitehorse LGA) to 0.0% (Manningham and Yarra LGAs).

- The number of people who have been told by a doctor or nurse that they have kidney disease was highest for people aged 60-69 years for both males and females, and the percentage of people who have been told by a doctor or nurse that they have kidney disease increased with increasing age.
:::

\newpage

```{r}
# Figure 10H-1
f_caption_figure("(A) Number and (B) percentage of people who identified as Aboriginal and/or Torres Strait Islander and who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by LGA, 2021")

figure_number <- health_kidney_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_lga(y_variable = aboriginal_n,
              y_max      = NA,
              y_breaks   = 5,
              y_expand   = 4.5,
              y_title    = "Number of people",
              plot_tag   = "A")

figure_percent <- health_kidney_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_lga(y_variable = aboriginal_prop,
              y_max      = 5,
              y_breaks   = 0.5,
              y_expand   = 0.125,
              y_title    = "Percentage of people",
              plot_tag   = "B")

figure_number + figure_percent
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

```{r}
# Figure 10H-2
f_caption_figure("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by LGA, 2021")

health_kidney_lga %>% 
  dplyr::filter(lga_name %in% nephu_lga) %>% 
  #
  f_graph_expected(variable = lga_name,
                   y_breaks = 5,
                   y_expand = 4.5)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

\newpage

```{r}
# Table 10H-1
f_caption_table("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by LGA, 2021")

health_kidney_lga %>% 
  dplyr::filter(lga_name %in% c(nephu_lga, "NEPHU")) %>%
  #
  f_table_expected(variable       = lga_name,
                   variable_label = "LGA",
                   group_label    = " ",
                   total_row      = 13)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`
:::

\newpage

```{r}
# Figure 10H-3
f_caption_figure("(A) Number and (B) percentage of people who identified as Aboriginal and/or Torres Strait Islander and who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by age and sex, 2021")

figure_female_number <- health_kidney_agesex %>%
  f_graph_agesex(sex        = "Female",
                 y_variable = aboriginal_n,
                 y_max      = 16,
                 y_breaks   = 2,
                 y_expand   = 0.25,
                 y_title    = "Number of females",
                 plot_title = "Females",
                 plot_tag   = "A")

figure_female_percent <- health_kidney_agesex %>%
  f_graph_agesex(sex        = "Female",
                 y_variable = aboriginal_prop,
                 y_max      = 10,
                 y_breaks   = 1,
                 y_expand   = 0.125,
                 y_title    = "Percentage of females",
                 plot_title = " ",
                 plot_tag   = "B")

figure_male_number <- health_kidney_agesex %>%
  f_graph_agesex(sex        = "Male",
                 y_variable = aboriginal_n,
                 y_max      = 16,
                 y_breaks   = 2,
                 y_expand   = 0.25,
                 y_title    = "Number of males",
                 plot_title = "Males",
                 plot_tag   = "A")

figure_male_percent <- health_kidney_agesex %>%
  f_graph_agesex(sex        = "Male",
                 y_variable = aboriginal_prop,
                 y_max      = 10,
                 y_breaks   = 1,
                 y_expand   = 0.125,
                 y_title    = "Percentage of males",
                 plot_title = " ",
                 plot_tag   = "B")

figure_female_number + figure_female_percent
figure_male_number + figure_male_percent
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

```{r} 
# Figure 10H-4
f_caption_figure("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by age and sex, 2021") 

health_kidney_agesex %>%  
  dplyr::filter(age_group %in% age_group_lvl) %>%  
  # 
  dplyr::mutate(age_group = factor(age_group, levels = age_group_lvl)) %>% 
  #
  f_graph_expected(variable = age_group, 
                   y_breaks = 2, 
                   y_expand = 0.5) +
  #
  facet_wrap(~sex,
             axes = "all")
``` 

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

```{r} 
# Table 10H-2
f_caption_table("Observed vs. expected number of Aboriginal and/or Torres Strait Islander people who have been told by a doctor or nurse that they have kidney disease, NEPHU catchment, by age and sex, 2021") 

health_kidney_agesex %>% 
  dplyr::filter(sex == "Female") %>%  
  # 
  f_table_expected(variable       = age_group,
                   variable_label = "Age group",
                   group_label    = "Females",
                   total_row      = 12)
  
health_kidney_agesex %>% 
  dplyr::filter(sex == "Male") %>%  
  # 
  f_table_expected(variable       = age_group,
                   variable_label = "Age group",
                   group_label    = "Males",
                   total_row      = 12)
``` 

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_census)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_unknown_agesex)`
:::

\newpage

## Hospital Admissions - Chronic Kidney Disease

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Hospitalisations - chronic kidney disease
# Data from PHIDU Social Health Atlas
# ------------------------------------------------------------------------------
# Read in PHIDU data
hospital_kidney <- f_read_phidu_iare_hospital(data_sheet    = "Admissions_principal_diag",
                                              column_select = "admissions_for_chronic_kidney_disease_aboriginal_people")

# Data wrangling
hospital_kidney <- hospital_kidney %>% 
  dplyr::mutate(iare_name = factor(iare_name, levels = iare_inc_vic_lvl),
                #
                hospital_n_label = round(hospital_n, digits = 0),
                #
                hospital_n_label = dplyr::case_when(
                  is.na(hospital_n) ~ "*",
                  TRUE ~ format(hospital_n_label, big.mark = ",")),
                #
                hospital_rate_label = round(hospital_rate, digits = 0),
                #
                hospital_rate_label = dplyr::case_when(
                  is.na(hospital_rate) ~ "*",
                  TRUE ~ format(hospital_rate_label, big.mark = ",")),
                #
                hospital_ratio_label = round(hospital_ratio, digits = 1),
                #
                hospital_ratio_label = dplyr::case_when(
                  is.na(hospital_ratio) ~ "*",
                  TRUE ~ format(hospital_ratio_label, big.mark = ","))) %>% 
  #
  dplyr::select(iare_name,
                iare_name_short,
                starts_with("hospital")) %>% 
  #
  dplyr::arrange(iare_name)
```


```{r}
results <- list()

data <- hospital_kidney %>% 
  dplyr::rename(n     = hospital_n,
                rate  = hospital_rate,
                ratio = hospital_ratio)

results$rank_n <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::select(iare_name,
                n)

results$rank_rate <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(rate)) %>% 
  dplyr::select(iare_name,
                rate)

results$rank_ratio <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(ratio)) %>% 
  dplyr::select(iare_name,
                ratio)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the PHIDU Social Health Atlas, compiled from the Victorian Admitted Episodes Dataset.

- During the four-year period 01 July 2017 to 30 June 2021 there were 293 hospital admissions for chronic kidney disease for Aboriginal and/or Torres Strait Islander people living in Greater Melbourne.

- The number of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 55 (Northcote/Preston/Whittlesea IARE) to 5 (Whitehorse and Yarra Ranges IAREs).

- The age-standardised rate of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 395 per 100,000 population (Maroondah IARE) to 58 per 100,000 population (Yarra Ranges IARE).

- 6 of the 8 IAREs in the NEPHU catchment area with data available for reporting had an age-standardised admission rate above the average for all Aboriginal and/or Torres Strait Islander people living in Greater Melbourne (Maroondah, Northcote/Preston/Whittlesea, Melbourne East, Whitehorse, Moreland/Broadmeadows, and Melbourne/Port Phillip IAREs).
:::

\newpage

```{r}
# Figure 10H-5
f_caption_figure("(A) Number and (B) age-standardised rate (per 100,000 population) of hospital admissions for chronic kidney disease for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

figure_number <- hospital_kidney %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_n,
               text_pos   = 1,
               y_label    = hospital_n_label,
               y_max      = NA,
               y_breaks   = 5,
               y_expand   = 1,
               y_title    = "Number of admissions",
               plot_tag   = "A")

figure_rate <- hospital_kidney %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_rate,
               text_pos   = 10,
               y_label    = hospital_rate_label,
               y_max      = NA,
               y_breaks   = 50,
               y_expand   = 15,
               y_title    = "Age-standardised rate",
               plot_tag   = "B")

figure_number + figure_rate
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_suppress)`

- Admissions for 'chronic kidney disease' are defined as those with a principal diagnosis code from the following list, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Infectious and parasitic diseases (B52.0 *Plasmodium malariae* malaria with nephropathy)
    
    - Haemolytic anaemias (D59.3 Haemolytic-uraemic syndrome)

    - Diabetes mellitus (E10.2 Type 1 diabetes mellitus with renal complications; E11.2 Type 2 diabetes mellitus with renal complications; E13.2 Other specified diabetes mellitus with renal complications; E14.2 Unspecified diabetes mellitus with renal complications)
    
    - Metabolic disorders (E85.1 Neuropathic heredofamilial amyloidosis)
    
    - Hypertensive diseases (I12 Hypertensive renal disease; I13 Hypertensive heart and renal disease; I15.0 Renovascular hypertension; I15.1 Hypertension secondary to other renal disorders)
    
    - Glomerular diseases (N00 Acute nephritic syndrome; N01 Rapidly progressive nephritic syndrome; N02 Recurrent and persistent haematuria; N03 Chronic nephritic syndrome; N04 Nephrotic syndrome; N05 Unspecified nephritic syndrome; N06 Isolated proteinuria with specified morphological lesion; N07 Hereditary nephropathy, not elsewhere classified; N08 Glomerular disorders in diseases classified elsewhere)
    
    - Renal tubulo-interstitial diseases (N11 Chronic tubulo-interstitial nephritis; N12 Tubulo-interstitial nephritis, not specified as acute or chronic; N14 Drug and heavy metal induced tubulo-interstitial and tubular conditions; N15 Other renal tubulo-interstitial diseases; N16 Renal tubulo-interstitial disorders in diseases classified elsewhere)
    
    - Renal failure (N18 Chronic kidney disease; N19 Unspecified kidney failure)
    
    - Other disorders of kidney and ureter (N25 Disorders resulting from impaired renal tubular function; N26 Unspecified contracted kidney; N27 Small kidney of unknown cause; N28 Other disorders of kidney and ureter, not elsewhere classified)
    
    - Other diseases of urinary system (N39.1 Persistent proteinuria, unspecified; N39.2 Orthostatic proteinuria, unspecified)
    
    - Congenital malformations of the urinary system (Q60 Renal agenesis and other reduction defects of kidney; Q61 Cystic kidney disease; Q62 Congenital obstructive defects of renal pelvis and congenital malformations of ureter; Q63 Other congenital malformations of kidney)
    
    - Complications of surgical and medical care (T82.4 Mechanical complication of vascular dialysis catheter; T86.1 Kidney transplant failure and rejection)
    
    - Care involving dialysis (Z49.0 Preparatory care for dialysis)

- Day admissions for extracorporeal dialysis (Z49.1) or other dialysis (Z49.2) are excluded.
:::

```{r}
# Table 10H-3
f_caption_table("Hospital admissions for chronic kidney disease for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

hospital_kidney %>% 
  dplyr::select(iare_name,
                hospital_n_label,
                hospital_rate_label,
                hospital_ratio_label) %>%
  #
  f_table_iare(table_headers = c("Number of\nadmissions", "Age-standardised rate\n(per 100,000)", "Standardised\nratio"),
               last_column   = 4) %>% 
  #
  flextable::width(j = 3,
                   width = 1.75)
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_ratio)`

`r knitr::asis_output(note_caveat_iare_suppress)`

- Admissions for 'chronic kidney disease' are defined as those with a principal diagnosis code from the following list, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Infectious and parasitic diseases (B52.0 *Plasmodium malariae* malaria with nephropathy)
    
    - Haemolytic anaemias (D59.3 Haemolytic-uraemic syndrome)

    - Diabetes mellitus (E10.2 Type 1 diabetes mellitus with renal complications; E11.2 Type 2 diabetes mellitus with renal complications; E13.2 Other specified diabetes mellitus with renal complications; E14.2 Unspecified diabetes mellitus with renal complications)
    
    - Metabolic disorders (E85.1 Neuropathic heredofamilial amyloidosis)
    
    - Hypertensive diseases (I12 Hypertensive renal disease; I13 Hypertensive heart and renal disease; I15.0 Renovascular hypertension; I15.1 Hypertension secondary to other renal disorders)
    
    - Glomerular diseases (N00 Acute nephritic syndrome; N01 Rapidly progressive nephritic syndrome; N02 Recurrent and persistent haematuria; N03 Chronic nephritic syndrome; N04 Nephrotic syndrome; N05 Unspecified nephritic syndrome; N06 Isolated proteinuria with specified morphological lesion; N07 Hereditary nephropathy, not elsewhere classified; N08 Glomerular disorders in diseases classified elsewhere)
    
    - Renal tubulo-interstitial diseases (N11 Chronic tubulo-interstitial nephritis; N12 Tubulo-interstitial nephritis, not specified as acute or chronic; N14 Drug and heavy metal induced tubulo-interstitial and tubular conditions; N15 Other renal tubulo-interstitial diseases; N16 Renal tubulo-interstitial disorders in diseases classified elsewhere)
    
    - Renal failure (N18 Chronic kidney disease; N19 Unspecified kidney failure)
    
    - Other disorders of kidney and ureter (N25 Disorders resulting from impaired renal tubular function; N26 Unspecified contracted kidney; N27 Small kidney of unknown cause; N28 Other disorders of kidney and ureter, not elsewhere classified)
    
    - Other diseases of urinary system (N39.1 Persistent proteinuria, unspecified; N39.2 Orthostatic proteinuria, unspecified)
    
    - Congenital malformations of the urinary system (Q60 Renal agenesis and other reduction defects of kidney; Q61 Cystic kidney disease; Q62 Congenital obstructive defects of renal pelvis and congenital malformations of ureter; Q63 Other congenital malformations of kidney)
    
    - Complications of surgical and medical care (T82.4 Mechanical complication of vascular dialysis catheter; T86.1 Kidney transplant failure and rejection)
    
    - Care involving dialysis (Z49.0 Preparatory care for dialysis)

- Day admissions for extracorporeal dialysis (Z49.1) or other dialysis (Z49.2) are excluded.
:::

\newpage

## Same Day Hospital Admissions - Dialysis

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Hospitalisations - dialysis
# Data from PHIDU Social Health Atlas
# ------------------------------------------------------------------------------
# Read in PHIDU data
hospital_dialysis <- f_read_phidu_iare_hospital(data_sheet    = "Admissions_same_day_renal",
                                                column_select = "same_day_admissions_for_dialysis_for_kidney_disease_aboriginal_people")

# Data wrangling
hospital_dialysis <- hospital_dialysis %>% 
  dplyr::mutate(iare_name = factor(iare_name, levels = iare_inc_vic_lvl),
                #
                hospital_n_label = round(hospital_n, digits = 0),
                #
                hospital_n_label = dplyr::case_when(
                  is.na(hospital_n) ~ "*",
                  TRUE ~ format(hospital_n_label, big.mark = ",")),
                #
                hospital_rate_label = round(hospital_rate, digits = 0),
                #
                hospital_rate_label = dplyr::case_when(
                  is.na(hospital_rate) ~ "*",
                  TRUE ~ format(hospital_rate_label, big.mark = ",")),
                #
                hospital_ratio_label = round(hospital_ratio, digits = 1),
                #
                hospital_ratio_label = dplyr::case_when(
                  is.na(hospital_ratio) ~ "*",
                  TRUE ~ format(hospital_ratio_label, big.mark = ","))) %>% 
  #
  dplyr::select(iare_name,
                iare_name_short,
                starts_with("hospital")) %>% 
  #
  dplyr::arrange(iare_name)
```


```{r}
results <- list()

data <- hospital_dialysis %>% 
  dplyr::rename(n     = hospital_n,
                rate  = hospital_rate,
                ratio = hospital_ratio)

results$rank_n <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::select(iare_name,
                n)

results$rank_rate <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(rate)) %>% 
  dplyr::select(iare_name,
                rate)

results$rank_ratio <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(ratio)) %>% 
  dplyr::select(iare_name,
                ratio)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the PHIDU Social Health Atlas, compiled from the Victorian Admitted Episodes Dataset.

- During the four-year period 01 July 2017 to 30 June 2021 there were 9,786 same day hospital admissions for dialysis for Aboriginal and/or Torres Strait Islander people living in Greater Melbourne.

- The number of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 1,652 (Northcote/Preston/Whittlesea IARE) to 91 (Yarra Ranges IARE).

- The age-standardised rate of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 13,438 per 100,000 population (Melbourne/Port Phillip IARE) to 990 per 100,000 population (Yarra Ranges IARE).

- 3 of the 7 IAREs in the NEPHU catchment area with data available for reporting had an age-standardised admission rate above the average for all Aboriginal and/or Torres Strait Islander people living in Greater Melbourne (Melbourne/Port Phillip, Northcote/Preston/Whittlesea, and Craigieburn/Sunbury IAREs).
:::

\newpage

```{r}
# Figure 10H-6
f_caption_figure("(A) Number and (B) age-standardised rate (per 100,000 population) of same day hospital admissions for dialysis for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

figure_number <- hospital_dialysis %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_n,
               text_pos   = 25,
               y_label    = hospital_n_label,
               y_max      = NA,
               y_breaks   = 250,
               y_expand   = 125,
               y_title    = "Number of admissions",
               plot_tag   = "A")

figure_rate <- hospital_dialysis %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "Yes",
               y_variable = hospital_rate,
               text_pos   = 250,
               y_label    = hospital_rate_label,
               y_max      = NA,
               y_breaks   = 1500,
               y_expand   = 250,
               y_title    = "Age-standardised rate",
               plot_tag   = "B")

figure_number + figure_rate
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_suppress)`

- Admissions for 'dialysis' are defined as those with a principal diagnosis code of Z49.1 (haemodialysis) or Z49.2 (peritoneal dialysis), coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Same day admissions are those with an admission and separation date on the same calendar day.
    
    - Overnight admissions for preparatory care for dialysis (Z49.0) are excluded.
:::

\newpage

```{r}
# Table 10H-4
f_caption_table("Same day hospital admissions for dialysis for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

hospital_dialysis %>% 
  dplyr::select(iare_name,
                hospital_n_label,
                hospital_rate_label,
                hospital_ratio_label) %>%
  #
  f_table_iare(table_headers = c("Number of\nadmissions", "Age-standardised rate\n(per 100,000)", "Standardised\nratio"),
               last_column   = 4) %>% 
  #
  flextable::width(j = 3,
                   width = 1.75)
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_ratio)`

`r knitr::asis_output(note_caveat_iare_suppress)`

- Admissions for 'dialysis' are defined as those with a principal diagnosis code of Z49.1 (haemodialysis) or Z49.2 (peritoneal dialysis), coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en).

    - Same day admissions are those with an admission and separation date on the same calendar day.
    
    - Overnight admissions for preparatory care for dialysis (Z49.0) are excluded.
:::

