---
title: "NEPHU First Nations Population Profile"
subtitle: "Health Consequences: Infectious Diseases"
output:
  officedown::rdocx_document: 
    page_size:
      width: 8.27
      length: 11.69
    page_margins:
      bottom: 0.5
      top: 0.5
      right: 0.8
      left: 0.8
      gutter: 0
    reference_docx: Template.docx
    
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("NEPHU First Nations Profile - ", "10K Consequences Infectious ", format(Sys.Date(), "%Y-%m-%d")), output_dir = "../Output/Dev") })
---

```{r setup, include = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      #
                      fig.align  = "center",
                      fig.width  = 7,
                      fig.height = 3.5,
                      #
                      ft.align = "center",
                      #
                      dpi = 300,
                      #
                      fig.topcaption = TRUE,
                      #
                      cache = FALSE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(here,
               tidyverse,
               rlang,
               janitor,
               readxl,
               sf,
               flextable,
               colorRamps,
               officer,
               officedown,
               extrafont,
               ggnewscale,
               patchwork,
               glue,
               odbc,
               DBI)

# Uncomment and run these lines if you get any weird "missing font" errors
#extrafont::font_import()
#extrafont::loadfonts(device = "win")
```


```{r, include = FALSE}
#
source(here::here("Code", "00_Setup.R"))

source(here::here("Code", "Functions", "Data prep", "f_wrangle_phess.R"))
source(here::here("Code", "Functions", "Data prep", "f_read_phidu_iare_hospital.R"))

source(here::here("Code", "Functions", "Graphs", "f_graph_phess_counts.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_phess_rates.R"))
source(here::here("Code", "Functions", "Graphs", "f_graph_iare.R"))

source(here::here("Code", "Functions", "Tables", "f_table_phess.R"))
source(here::here("Code", "Functions", "Tables", "f_table_iare.R"))
```

**Table of Contents**

```{r}
#
block_toc(level = 2)
```

\newpage

```{r, include = FALSE}
# Numbering and styling for figures and tables
f_caption_figure <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Figure", 
                                                 pre_label = "Figure 10K-"))
  
  return(caption)
  
}

f_caption_table <- function(title_text) {
  
  caption <- block_caption(title_text, 
                           style   = "caption", 
                           autonum = run_autonum(seq_id    = "Table", 
                                                 pre_label = "Table 10K-"))
  
  return(caption)
  
}
```

### What infectious diseases affect Aboriginal and/or Torres Strait Islander people living in the NEPHU catchment?

```{r, include = FALSE}
# Read in PHESS data
cases_all <- read.csv(paste0(here::here(), "/Data", "/PHAR_Extract_2015_2024.csv")) 

# Data wrangling
cases_all <- cases_all %>% 
  dplyr::mutate(event_date = lubridate::ymd(event_date),
                year       = as.character(lubridate::year(event_date)),
                #
                lga = stringr::str_extract(lga, "^.*?(?=\\()"),
                lga = stringr::str_trim(lga),
                #
                nephu_case = dplyr::case_when(lga %in% nephu_lga ~ "NEPHU",
                                              TRUE ~ "Not NEPHU"),
                #
                indigenous_status = dplyr::case_when(
                  indigenous_status == "Aboriginal and Torres Strait Islander origin"     ~ "aboriginal",
                  indigenous_status == "Aboriginal but not Torres Strait Islander origin" ~ "aboriginal",
                  indigenous_status == "Torres Strait Islander but not Aboriginal origin" ~ "aboriginal",
                  indigenous_status == "Not Aboriginal or Torres Strait Islander"         ~ "non_aboriginal",
                  TRUE ~ "not_stated")) %>% 
  #
  dplyr::filter(indigenous_status != "not_stated")
```

# Vaccine Preventable Conditions

```{r, include = FALSE}
# ---------------------------------------------------------------------------------
# Notifiable conditions: vaccine preventable and respiratory diseases
# Data from PHESS
# ---------------------------------------------------------------------------------
conditions_vax_resp <- c("Diphtheria", "HiB", "Influenza", "Measles", "IMD", "Mumps",
                         "Pertussis",  "IPD", "RSV", "VZV")

cases_vaccine <- cases_all %>%
  dplyr::mutate(condition = dplyr::case_when(
    condition == "Haemophilus influenzae type B infection"  ~ "HiB",
    condition == "Meningococcal infection"                  ~ "IMD",
    condition == "Pneumococcal infection (IPD)"             ~ "IPD",
    condition == "Respiratory Syncytial virus"              ~ "RSV",
    condition == "Varicella zoster infection (Chickenpox)"  ~ "VZV",
    condition == "Varicella zoster infection (Shingles)"    ~ "VZV",
    condition == "Varicella zoster infection (Unspecified)" ~ "VZV",
    TRUE ~ condition)) %>% 
  #
  f_wrangle_phess(conditions_list = conditions_vax_resp)
```

::: {custom-style="Dotpt"}
- Data for these indicators were obtained from the Victorian Public Health Surveillance System.

- Data presented here are for notifications where Aboriginal and/or Torres Strait Islander status was known. The completeness of data on Aboriginal and/or Torres Strait Islander status varies across conditions and over time.

- Data broken down by Aboriginal and/or Torres Strait Islander status are publicly available for a selection of conditions at statewide level. Additional data may be made available upon request to the Victorian Department of Health.

- The number and rate of pertussis notifications decreased during the COVID-19 pandemic and rebounded significantly during 2024. This increase in 2024 was seen for both Aboriginal and/or Torres Strait Islander people and non-Indigenous people in both the NEPHU catchment and Victoria, and similar increases were seen across all other Australian states and territories.

- The most recent notification for invasive meningococcal disease (IMD) for an Aboriginal and/or Torres Strait Islander resident of the NEPHU catchment was in 2018. For Victoria overall, the number of notifications and notification rates have decreased in the years following the COVID-19 pandemic, however the rates of IMD remain higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people.

- The notification rates of invasive pneumococcal disease (IPD) were consistently higher for the NEPHU catchment compared to Victoria overall for both Aboriginal and/or Torres Strait Islander people and non-Indigenous people. The rates of IPD were also consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people.

- The number and rates of Varicella Zoster notifications in the years following the COVID-19 pandemic remained lower than for pre-pandemic years for Aboriginal and/or Torres Strait Islander people residing in the NEPHU catchment but have since rebounded to pre-pandemic levels for Aboriginal and/or Torres Strait Islander people in Victoria and for non-Indigenous people.
:::

\newpage

## Pertussis

```{r}
# Figure 10K-1
f_caption_figure("Number of pertussis notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_vaccine %>%
  f_graph_phess_counts(condition_name = "Pertussis",
                       y_max          = NA,
                       y_breaks       = 20,
                       y_expand       = 20)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- The following pertussis notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <12 months
  
  - Women known to be in the last month of pregnancy
  
  - Persons known to be in contact with children aged <6 months or women in the last month of pregnancy
  
  - Persons known to attend or work in settings where there is likely to be contact with children aged <6 months or women in the last month of pregnancy
  
- Depending on operational capacity, children aged <5 years and children aged <10 years should also be followed up.

- The management of pertussis transitioned from the Victorian Department of Health to Local Public Health Units on 18/07/2022.
:::

\newpage

```{r}
# Figure 10K-2
f_caption_figure("Pertussis notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_vaccine %>% 
  dplyr::filter(condition == "Pertussis") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 275,
                      y_breaks   = 25,
                      y_expand   = 5)

figure_vic <- cases_vaccine %>% 
  dplyr::filter(condition == "Pertussis") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 275,
                      y_breaks   = 25,
                      y_expand   = 5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- The following pertussis notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <12 months
  
  - Women known to be in the last month of pregnancy
  
  - Persons known to be in contact with children aged <6 months or women in the last month of pregnancy
  
  - Persons known to attend or work in settings where there is likely to be contact with children aged <6 months or women in the last month of pregnancy
  
- Depending on operational capacity, children aged <5 years and children aged <10 years should also be followed up.

- The management of pertussis transitioned from the Victorian Department of Health to Local Public Health Units on 18/07/2022.
:::

\newpage

```{r}
# Table 10K-1
f_caption_table("Number of pertussis notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_vaccine %>% 
  f_table_phess(condition_name = "Pertussis")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- The following pertussis notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <12 months
  
  - Women known to be in the last month of pregnancy
  
  - Persons known to be in contact with children aged <6 months or women in the last month of pregnancy
  
  - Persons known to attend or work in settings where there is likely to be contact with children aged <6 months or women in the last month of pregnancy
  
- Depending on operational capacity, children aged <5 years and children aged <10 years should also be followed up.

- The management of pertussis transitioned from the Victorian Department of Health to Local Public Health Units on 18/07/2022.
:::

\newpage

## Invasive Meningococcal Disease (IMD)

```{r}
# Figure 10K-3
f_caption_figure("Number of invasive meningococcal disease notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_vaccine %>%
  f_graph_phess_counts(condition_name = "IMD",
                       y_max          = 5,
                       y_breaks       = 1,
                       y_expand       = 0.125)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All invasive meningococcal disease notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- The management of invasive meningococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 27/02/2023.
:::

\newpage

```{r}
# Figure 10K-4
f_caption_figure("Invasive meningococcal disease notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_vaccine %>% 
  dplyr::filter(condition == "IMD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 10,
                      y_breaks   = 1,
                      y_expand   = 0.125)

figure_vic <- cases_vaccine %>% 
  dplyr::filter(condition == "IMD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 10,
                      y_breaks   = 1,
                      y_expand   = 0.125)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive meningococcal disease notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- The management of invasive meningococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 27/02/2023.
:::

\newpage

```{r}
# Table 10K-2
f_caption_table("Number of invasive meningococcal disease notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_vaccine %>% 
  f_table_phess(condition_name = "IMD")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive meningococcal disease notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- The management of invasive meningococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 27/02/2023.
:::

\newpage

## Invasive Pneumococcal Disease (IPD)

```{r}
# Figure 10K-5
f_caption_figure("Number of invasive pneumococcal disease notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_vaccine %>%
  f_graph_phess_counts(condition_name = "IPD",
                       y_max          = NA,
                       y_breaks       = 2,
                       y_expand       = 1.5)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All invasive pneumococcal disease notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of invasive pneumococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

```{r}
# Figure 10K-6
f_caption_figure("Invasive pneumococcal disease notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_vaccine %>% 
  dplyr::filter(condition == "IPD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 40,
                      y_breaks   = 5,
                      y_expand   = 1)

figure_vic <- cases_vaccine %>% 
  dplyr::filter(condition == "IPD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 40,
                      y_breaks   = 5,
                      y_expand   = 1)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive pneumococcal disease notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of invasive pneumococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

```{r}
# Table 10K-3
f_caption_table("Number of invasive pneumococcal disease notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_vaccine %>% 
  f_table_phess(condition_name = "IPD")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive pneumococcal disease notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of invasive pneumococcal disease transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

## Varicella Zoster

```{r}
# Figure 10K-7
f_caption_figure("Number of Varicella Zoster notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_vaccine %>%
  f_graph_phess_counts(condition_name = "VZV",
                       y_max          = NA,
                       y_breaks       = 10,
                       y_expand       = 2)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- 'Varicella Zoster' includes chickenpox, shingles, and unspecified notifications.

- The following Varicella Zoster notifications are signed out for case management and follow-up by Local Public Health Units:

  - Inpatients and staff of high-risk healthcare settings (e.g. immunosuppressive wards, neonatal wards, obstetric wards)
  
  - Persons known to have exposed high-risk groups (e.g. neonates, pregnant women, immunosuppressed individuals)
  
  - Persons linked to an outbreak in a high-risk setting (e.g. healthcare facilities, aged care facilities, childcare facilities, schools)

- The management of Varicella Zoster transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

```{r}
# Figure 10K-8
f_caption_figure("Varicella Zoster notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_vaccine %>% 
  dplyr::filter(condition == "VZV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 140,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_vic <- cases_vaccine %>% 
  dplyr::filter(condition == "VZV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 140,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Varicella Zoster' includes chickenpox, shingles, and unspecified notifications.

- The following Varicella Zoster notifications are signed out for case management and follow-up by Local Public Health Units:

  - Inpatients and staff of high-risk healthcare settings (e.g. immunosuppressive wards, neonatal wards, obstetric wards)
  
  - Persons known to have exposed high-risk groups (e.g. neonates, pregnant women, immunosuppressed individuals)
  
  - Persons linked to an outbreak in a high-risk setting (e.g. healthcare facilities, aged care facilities, childcare facilities, schools)

- The management of Varicella Zoster transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

```{r}
# Table 10K-4
f_caption_table("Number of Varicella Zoster notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_vaccine %>% 
  f_table_phess(condition_name = "VZV")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Varicella Zoster' includes chickenpox, shingles, and unspecified notifications.

- The following Varicella Zoster notifications are signed out for case management and follow-up by Local Public Health Units:

  - Inpatients and staff of high-risk healthcare settings (e.g. immunosuppressive wards, neonatal wards, obstetric wards)
  
  - Persons known to have exposed high-risk groups (e.g. neonates, pregnant women, immunosuppressed individuals)
  
  - Persons linked to an outbreak in a high-risk setting (e.g. healthcare facilities, aged care facilities, childcare facilities, schools)

- The management of Varicella Zoster transitioned from the Victorian Department of Health to Local Public Health Units on 15/08/2022.
:::

\newpage

# Bloodborne Viruses

```{r, include = FALSE}
# ---------------------------------------------------------------------------------
# Notifiable conditions: BBV and STI
# Data from PHESS
# ---------------------------------------------------------------------------------
conditions_bbv_sti <- c("Chlamydia", "Gonococcal", "Mpox", "Syphilis - Congenital",
                        "Syphilis - Infectious", "Syphilis - Late", "HBV", "HCV", "HIV")

cases_bbvsti <- cases_all %>% 
  dplyr::mutate(condition = dplyr::case_when(
    condition == "Chlamydia trachomatis infection" ~ "Chlamydia",
    condition == "Gonococcal infection"            ~ "Gonococcal",
    condition == "Hepatitis B - Newly acquired"    ~ "HBV",
    condition == "Hepatitis B - Unspecified"       ~ "HBV",
    condition == "Hepatitis C - <24 months of age" ~ "HCV",
    condition == "Hepatitis C - Newly acquired"    ~ "HCV",
    condition == "Hepatitis C - Unspecified"       ~ "HCV",
    #
    condition == "Human Immunodeficiency Virus Infection - Child aged less than 18 months"     ~ "HIV",
    condition == "Human Immunodeficiency Virus Infection - Individual aged 18 months or older" ~ "HIV",
    TRUE ~ condition)) %>% 
  #
  f_wrangle_phess(conditions_list = conditions_bbv_sti)
```

::: {custom-style="Dotpt"}
- Data for these indicators were obtained from the Victorian Public Health Surveillance System.

- Data presented here are for notifications where Aboriginal and/or Torres Strait Islander status was known. The completeness of data on Aboriginal and/or Torres Strait Islander status varies across conditions and over time.

- Data broken down by Aboriginal and/or Torres Strait Islander status are publicly available for a selection of conditions at statewide level. Additional data may be made available upon request to the Victorian Department of Health.

- The number and rate of hepatitis B notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have not rebounded to pre-pandemic levels. Since the COVID-19 pandemic, notification rates have been consistently lower for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- The number and rate of hepatitis C notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have since rebounded to pre-pandemic levels. Notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- The number and rate of HIV notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have since increased but remain lower than pre-pandemic levels. Notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.
:::

\newpage

## Hepatitis B

```{r}
# Figure 10K-9
f_caption_figure("Number of hepatitis B notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "HBV",
                       y_max          = NA,
                       y_breaks       = 1,
                       y_expand       = 0.25)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- 'Hepatitis B' includes newly acquired and unspecified notifications.

- The following hepatitis B notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <24 months
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF
  
- The management of hepatitis B transitioned from the Victorian Department of Health to Local Public Health Units on 29/08/2022.
:::

\newpage

```{r}
# Figure 10K-10
f_caption_figure("Hepatitis B notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "HBV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 25,
                      y_breaks   = 5,
                      y_expand   = 0.5)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "HBV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 25,
                      y_breaks   = 5,
                      y_expand   = 0.5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Hepatitis B' includes newly acquired and unspecified notifications.

- The following hepatitis B notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <24 months
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF
  
- The management of hepatitis B transitioned from the Victorian Department of Health to Local Public Health Units on 29/08/2022.
:::

\newpage

```{r}
# Table 10K-5
f_caption_table("Number of hepatitis B notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "HBV")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Hepatitis B' includes newly acquired and unspecified notifications.

- The following hepatitis B notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <24 months
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF
  
- The management of hepatitis B transitioned from the Victorian Department of Health to Local Public Health Units on 29/08/2022.
:::

\newpage

## Hepatitis C

```{r}
# Figure 10K-11
f_caption_figure("Number of hepatitis C notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "HCV",
                       y_max          = NA,
                       y_breaks       = 20,
                       y_expand       = 2)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- 'Hepatitis C' includes newly acquired and unspecified notifications.

- The following hepatitis C notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF

- The management of hepatitis C transitioned from the Victorian Department of Health to Local Public Health Units on 05/09/2022.
:::

\newpage

```{r}
# Figure 10K-12
f_caption_figure("Hepatitis C notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "HCV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 200,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "HCV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 200,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Hepatitis C' includes newly acquired and unspecified notifications.

- The following hepatitis C notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF

- The management of hepatitis C transitioned from the Victorian Department of Health to Local Public Health Units on 05/09/2022.
:::

\newpage

```{r}
# Table 10K-6
f_caption_table("Number of hepatitis C notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "HCV")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Hepatitis C' includes newly acquired and unspecified notifications.

- The following hepatitis C notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years
  
  - Persons with potential newly acquired infections
  
  - Persons with potential occult infections 
  
  - Persons with potential false positive laboratory results
  
  - Persons undergoing screening for onshore visa renewal or offshore health undertaking
  
  - Persons known to have high-risk exposures (e.g. medical procedures, blood transfusion, tattooing) or work in high-risk settings (e.g. healthcare workers)
  
  - Women known to be pregnant or undergoing IVF

- The management of hepatitis C transitioned from the Victorian Department of Health to Local Public Health Units on 05/09/2022.
:::

\newpage

## Human Immunodeficiency Virus (HIV)

```{r}
# Figure 10K-13
f_caption_figure("Number of HIV notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "HIV",
                       y_max          = NA,
                       y_breaks       = 1,
                       y_expand       = 0.25)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All HIV notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of HIV transitioned from the Victorian Department of Health to Local Public Health Units on 09/08/2023.
:::

\newpage

```{r}
# Figure 10K-14
f_caption_figure("HIV notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "HIV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 18,
                      y_breaks   = 2,
                      y_expand   = 0.5)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "HIV") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 18,
                      y_breaks   = 2,
                      y_expand   = 0.5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All HIV notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of HIV transitioned from the Victorian Department of Health to Local Public Health Units on 09/08/2023.
:::

\newpage

```{r}
# Table 10K-7
f_caption_table("Number of HIV notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "HIV")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All HIV notifications are signed out for case management and follow-up by Local Public Health Units.

- The management of HIV transitioned from the Victorian Department of Health to Local Public Health Units on 09/08/2023.
:::

\newpage

# Sexually Transmissible Infections

::: {custom-style="Dotpt"}
- Data for these indicators were obtained from the Victorian Public Health Surveillance System.

- Data presented here are for notifications where Aboriginal and/or Torres Strait Islander status was known. The completeness of data on Aboriginal and/or Torres Strait Islander status varies across conditions and over time.

- Data broken down by Aboriginal and/or Torres Strait Islander status are publicly available for a selection of conditions at statewide level. Additional data may be made available upon request to the Victorian Department of Health.

- The number and rate of gonorrhoea notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have since rebounded to higher than pre-pandemic levels. Notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- The number and rate of infectious syphilis notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have since rebounded to higher than pre-pandemic levels. Notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- The number and rate of late syphilis notifications decreased for Aboriginal and/or Torres Strait Islander people during the COVID-19 pandemic and have since rebounded to higher than pre-pandemic levels. Notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- The most recent notification for congenital syphilis for an Aboriginal and/or Torres Strait Islander resident of the NEPHU catchment was in 2020. For Victoria overall, notification rates were consistently higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people.
:::

\newpage

## Gonorrhoea

```{r}
# Figure 10K-15
f_caption_figure("Number of gonorrhoea notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "Gonococcal",
                       y_max          = NA,
                       y_breaks       = 20,
                       y_expand       = 20)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- The following gonorrhoea notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years

  - Women known to be pregnant
  
  - Persons with decreased susceptibility to ceftriaxone, critical antimicrobial resistant, or extensively drug resistant gonorrhoea
  
- The management of gonorrhoea transitioned from the Victorian Department of Health to Local Public Health Units on 30/01/2023.
:::

\newpage

```{r}
# Figure 10K-16
f_caption_figure("Gonorrhoea notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "Gonococcal") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 275,
                      y_breaks   = 25,
                      y_expand   = 5)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "Gonococcal") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 275,
                      y_breaks   = 25,
                      y_expand   = 5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- The following gonorrhoea notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years

  - Women known to be pregnant
  
  - Persons with decreased susceptibility to ceftriaxone, critical antimicrobial resistant, or extensively drug resistant gonorrhoea
  
- The management of gonorrhoea transitioned from the Victorian Department of Health to Local Public Health Units on 30/01/2023.
:::

\newpage

```{r}
# Table 10K-8
f_caption_table("Number of gonorrhoea notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "Gonococcal")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- The following gonorrhoea notifications are signed out for case management and follow-up by Local Public Health Units:

  - Children aged <16 years

  - Women known to be pregnant
  
  - Persons with decreased susceptibility to ceftriaxone, critical antimicrobial resistant, or extensively drug resistant gonorrhoea
  
- The management of gonorrhoea transitioned from the Victorian Department of Health to Local Public Health Units on 30/01/2023.
:::

\newpage

## Infectious Syphilis

```{r}
# Figure 10K-17
f_caption_figure("Number of infectious syphilis notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "Syphilis - Infectious",
                       y_max          = NA,
                       y_breaks       = 10,
                       y_expand       = 4)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- 'Infectious syphilis' is defined as syphilis of less than two years duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Figure 10K-18
f_caption_figure("Infectious syphilis notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Infectious") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 120,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Infectious") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 120,
                      y_breaks   = 20,
                      y_expand   = 5)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Infectious syphilis' is defined as syphilis of less than two years duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Table 10K-9
f_caption_table("Number of infectious syphilis notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "Syphilis - Infectious")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Infectious syphilis' is defined as syphilis of less than two years duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

## Late Syphilis

```{r}
# Figure 10K-19
f_caption_figure("Number of late syphilis notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "Syphilis - Late",
                       y_max          = NA,
                       y_breaks       = 5,
                       y_expand       = 2)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- 'Late syphilis' is defined as syphilis of more than two years or unknown duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Figure 10K-20
f_caption_figure("Late syphilis notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Late") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 60,
                      y_breaks   = 10,
                      y_expand   = 2)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Late") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 60,
                      y_breaks   = 10,
                      y_expand   = 2)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Late syphilis' is defined as syphilis of more than two years or unknown duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Table 10K-10
f_caption_table("Number of late syphilis notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "Syphilis - Late")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- 'Late syphilis' is defined as syphilis of more than two years or unknown duration.

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

## Congenital Syphilis

```{r}
# Figure 10K-21
f_caption_figure("Number of congenital syphilis notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_bbvsti %>%
  f_graph_phess_counts(condition_name = "Syphilis - Congenital",
                       y_max          = 5,
                       y_breaks       = 1,
                       y_expand       = 0.25)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Figure 10K-22
f_caption_figure("Congenital syphilis notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Congenital") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 10,
                      y_breaks   = 1,
                      y_expand   = 0.25)

figure_vic <- cases_bbvsti %>% 
  dplyr::filter(condition == "Syphilis - Congenital") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 10,
                      y_breaks   = 1,
                      y_expand   = 0.25)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

```{r}
# Table 10K-11
f_caption_table("Number of congenital syphilis notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_bbvsti %>% 
  f_table_phess(condition_name = "Syphilis - Congenital") %>% 
  #
  flextable::colformat_double(j = c(3, 5, 7, 9),
                              digits = 2)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All syphilis notifications are signed out for case management and follow-up by Local Public Health Units, with the following groups prioritised for follow-up:

  - Women known to be pregnant
  
  - Suspected, confirmed, or probable cases of congenital syphilis

  - Children aged <16 years
  
  - Women of reproductive age (aged 15-49 years)
  
  - Aboriginal and/or Torres Strait Islander people
  
  - Partners of cases who are known to be pregnant

- The management of syphilis transitioned from the Victorian Department of Health to Local Public Health Units on 03/04/2023.
:::

\newpage

# Other Conditions

```{r, include = FALSE}
# ---------------------------------------------------------------------------------
# Notifiable conditions: other conditions
# Data from PHESS
# ---------------------------------------------------------------------------------
conditions_other <- c("ARF", "iGAS", "Legionellosis", "RHD")

cases_other <- cases_all %>% 
  dplyr::mutate(condition = dplyr::case_when(
    condition == "Acute Rheumatic Fever"          ~ "ARF",
    condition == "Invasive Group A Streptococcus" ~ "iGAS",
    condition == "Rheumatic Heart Disease"        ~ "RHD",
    TRUE ~ condition)) %>% 
  #
  f_wrangle_phess(conditions_list = conditions_other)
```

::: {custom-style="Dotpt"}
- Data for these indicators were obtained from the Victorian Public Health Surveillance System.

- Data presented here are for notifications where Aboriginal and/or Torres Strait Islander status was known. The completeness of data on Aboriginal and/or Torres Strait Islander status varies across conditions and over time.

- Data broken down by Aboriginal and/or Torres Strait Islander status are publicly available for a selection of conditions at statewide level. Additional data may be made available upon request to the Victorian Department of Health.

- Invasive Group A *Streptococcus* became notifiable in Victoria in February 2022. Notification rates were higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for both the NEPHU catchment and Victoria.

- There have been no notifications of acute rheumatic fever in Aboriginal and/or Torres Strait Islander residents of the NEPHU catchment since it became notifiable in Victoria in July 2023. Notification rates were higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for Victoria overall.

- There have been no notifications of rheumatic heart disease in Aboriginal and/or Torres Strait Islander residents of the NEPHU catchment since it became notifiable in Victoria in July 2023. Notification rates were higher for Aboriginal and/or Torres Strait Islander people compared to non-Indigenous people for Victoria overall.
:::

\newpage

## Invasive Group A Streptococcus (iGAS)

```{r}
# Figure 10K-23
f_caption_figure("Number of invasive Group A Streptococcus notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_other %>%
  f_graph_phess_counts(condition_name = "iGAS",
                       y_max          = NA,
                       y_breaks       = 1,
                       y_expand       = 0.5)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All invasive Group A *Streptococcus* notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- Invasive Group A *Streptococcus* became a notifiable condition in Victoria on 22/02/2022 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 31/05/2023.
:::

\newpage

```{r}
# Figure 10K-24
f_caption_figure("Invasive Group A Streptococcus notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_other %>% 
  dplyr::filter(condition == "iGAS") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 20,
                      y_breaks   = 2,
                      y_expand   = 1)

figure_vic <- cases_other %>% 
  dplyr::filter(condition == "iGAS") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 20,
                      y_breaks   = 2,
                      y_expand   = 1)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive Group A *Streptococcus* notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- Invasive Group A *Streptococcus* became a notifiable condition in Victoria on 22/02/2022 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 31/05/2023.
:::

\newpage

```{r}
# Table 10K-12
f_caption_table("Number of invasive Group A Streptococcus notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_other %>% 
  f_table_phess(condition_name = "iGAS")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All invasive Group A *Streptococcus* notifications are signed out for urgent case management and follow-up by Local Public Health Units.

- Invasive Group A *Streptococcus* became a notifiable condition in Victoria on 22/02/2022 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 31/05/2023.
:::

\newpage

## Acute Rheumatic Fever

```{r}
# Figure 10K-25
f_caption_figure("Number of acute rheumatic fever notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_other %>%
  f_graph_phess_counts(condition_name = "ARF",
                       y_max          = 5,
                       y_breaks       = 1,
                       y_expand       = 0.25)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All acute rheumatic fever notifications are signed out for case management and follow-up by Local Public Health Units.

- Acute rheumatic fever became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

```{r}
# Figure 10K-26
f_caption_figure("Acute rheumatic fever notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_other %>% 
  dplyr::filter(condition == "ARF") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 7,
                      y_breaks   = 1,
                      y_expand   = 0.1)

figure_vic <- cases_other %>% 
  dplyr::filter(condition == "ARF") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 7,
                      y_breaks   = 1,
                      y_expand   = 0.1)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All acute rheumatic fever notifications are signed out for case management and follow-up by Local Public Health Units.

- Acute rheumatic fever became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

```{r}
# Table 10K-13
f_caption_table("Number of acute rheumatic fever notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_other %>% 
  f_table_phess(condition_name = "ARF")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All acute rheumatic fever notifications are signed out for case management and follow-up by Local Public Health Units.

- Acute rheumatic fever became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

## Rheumatic Heart Disease

```{r}
# Figure 10K-27
f_caption_figure("Number of rheumatic heart disease notifications for Aboriginal and/or Torres Strait Islander people, Victoria, by year")

cases_other %>%
  f_graph_phess_counts(condition_name = "RHD",
                       y_max          = 5,
                       y_breaks       = 1,
                       y_expand       = 0.25)
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

- All rheumatic heart disease notifications are signed out for case management and follow-up by Local Public Health Units.

- Rheumatic heart disease became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

```{r}
# Figure 10K-28
f_caption_figure("Rheumatic heart disease notification rate for (A) NEPHU and (B) Victoria, by Aboriginal and/or Torres Strait Islander status and year")

figure_nephu <- cases_other %>% 
  dplyr::filter(condition == "RHD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "A",
                      y_variable = nephu_rate,
                      y_max      = 5,
                      y_breaks   = 1,
                      y_expand   = 0.25)

figure_vic <- cases_other %>% 
  dplyr::filter(condition == "RHD") %>% 
  #
  f_graph_phess_rates(plot_tag   = "B",
                      y_variable = vic_rate,
                      y_max      = 5,
                      y_breaks   = 1,
                      y_expand   = 0.25)

figure_nephu + figure_vic + 
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All rheumatic heart disease notifications are signed out for case management and follow-up by Local Public Health Units.

- Rheumatic heart disease became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

```{r}
# Table 10K-14
f_caption_table("Number of rheumatic heart disease notifications and notification rate, NEPHU and Victoria, by Aboriginal and/or Torres Strait Islander status and year")

cases_other %>% 
  f_table_phess(condition_name = "RHD")
```

#### Data notes:
 
::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phess)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_notifiable_decrease)`

`r knitr::asis_output(note_caveat_notifiable_rate)`

- All rheumatic heart disease notifications are signed out for case management and follow-up by Local Public Health Units.

- Rheumatic heart disease became a notifiable condition in Victoria on 31/07/2023 and the management of notifications transitioned from the Victorian Department of Health to Local Public Health Units on 02/08/2023.
:::

\newpage

# Hospital Admissions

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Hospitalisations - infectious and parasitic diseases
# Data from PHIDU Social Health Atlas
# ------------------------------------------------------------------------------
# Read in PHIDU data
hospital_infectious <- f_read_phidu_iare_hospital(data_sheet    = "Admissions_principal_diag",
                                                  column_select = "admissions_for_infectious_and_parasitic_diseases_aboriginal_people")

# Data wrangling
hospital_infectious <- hospital_infectious %>% 
  dplyr::mutate(iare_name = factor(iare_name, levels = iare_inc_vic_lvl)) %>% 
  #
  dplyr::select(iare_name,
                iare_name_short,
                starts_with("hospital")) %>% 
  #
  dplyr::arrange(iare_name)
```


```{r}
#
results <- list()

data <- hospital_infectious %>% 
  dplyr::rename(n     = hospital_n,
                rate  = hospital_rate,
                ratio = hospital_ratio)

results$rank_n <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::select(iare_name,
                n)

results$rank_rate <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(rate)) %>% 
  dplyr::select(iare_name,
                rate)

results$rank_ratio <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(ratio)) %>% 
  dplyr::select(iare_name,
                ratio)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the PHIDU Social Health Atlas, compiled from the Victorian Admitted Episodes Dataset.

- During the four-year period 01 July 2017 to 30 June 2021 there were 1,090 hospital admissions for infectious and parasitic diseases for Aboriginal and/or Torres Strait Islander people living in Greater Melbourne.

- The number of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 129 (Northcote/Preston/Whittlesea IARE) to 10 (Whitehorse IARE).

- The age-standardised rate of admissions for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 1,306 per 100,000 population (Melbourne/Port Phillip IARE) to 326 per 100,000 population (Melbourne East IARE).

- 6 of the 10 IAREs in the NEPHU catchment area had an age-standardised admission rate above the average for all Aboriginal and/or Torres Strait Islander people living in Greater Melbourne (Melbourne/Port Phillip, Knox, Craigieburn/Sunbury, Moreland/Broadmeadows, Melbourne North-East, and Northcote/Preston/Whittlesea IAREs).
:::

\newpage

```{r}
# Figure 10K-29
f_caption_figure("(A) Number and (B) age-standardised rate (per 100,000 population) of hospital admissions for infectious and parasitic diseases for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

figure_number <- hospital_infectious %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "No",
               y_variable = hospital_n,
               y_max      = NA,
               y_breaks   = 20,
               y_expand   = 15,
               y_title    = "Number of admissions",
               plot_tag   = "A")

figure_rate <- hospital_infectious %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "No",
               y_variable = hospital_rate,
               y_max      = NA,
               y_breaks   = 200,
               y_expand   = 125,
               y_title    = "Age-standardised rate",
               plot_tag   = "B")

figure_number + figure_rate
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

- Admissions for 'infectious and parasitic diseases' are defined as those with a principal diagnosis code between A00-B99, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en). The following major categories are included:

    - A00-A09: Intestinal infectious diseases
    
    - A15-A19: Tuberculosis
    
    - A20-A28: Certain zoonotic bacterial diseases
    
    - A30-A49: Other bacterial diseases
    
    - A50-A64: Infections with a predominantly sexual mode of transmission
    
    - A65-A69: Other spirochaetal diseases
    
    - A70-A74: Other diseases caused by chlamydiae
    
    - A75-A79: Rickettsioses
    
    - A80-A89: Viral infections of the central nervous system
    
    - A92-A99: Arthropod-borne viral fevers and viral haemorrhagic fevers
    
    - B00-B09: Viral infections characterized by skin and mucous membrane lesions
    
    - B15-B19: Viral hepatitis
    
    - B20-B24: Human immunodeficiency virus
    
    - B25-B34: Other viral diseases
    
    - B35-B49: Mycoses
    
    - B50-B64: Protozoal diseases
    
    - B65-B83: Helminthiases
    
    - B85-B89: Pediculosis, acariasis, and other infestations
    
    - B90-B94: Sequelae of infectious and parasitic diseases
    
    - B95-B98: Bacterial, viral, and other infectious agents
    
    - B99: Other and unspecified infectious diseases
:::

```{r}
# Table 10K-15
f_caption_table("Hospital admissions for infectious and parasitic diseases for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2017 to 30 June 2021")

hospital_infectious %>% 
  dplyr::select(-iare_name_short) %>% 
  #
  dplyr::mutate(hospital_rate  = round(hospital_rate, digits = 0),
                hospital_ratio = round(hospital_ratio, digits = 1)) %>% 
  #
  f_table_iare(table_headers = c("Number of\nadmissions", "Age-standardised rate\n(per 100,000)", "Standardised\nratio"),
               last_column   = 4) %>% 
  #
  flextable::width(j = 3,
                   width = 1.75)
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_ratio)`

- Admissions for 'infectious and parasitic diseases' are defined as those with a principal diagnosis code between A00-B99, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en). The following major categories are included:

    - A00-A09: Intestinal infectious diseases
    
    - A15-A19: Tuberculosis
    
    - A20-A28: Certain zoonotic bacterial diseases
    
    - A30-A49: Other bacterial diseases
    
    - A50-A64: Infections with a predominantly sexual mode of transmission
    
    - A65-A69: Other spirochaetal diseases
    
    - A70-A74: Other diseases caused by chlamydiae
    
    - A75-A79: Rickettsioses
    
    - A80-A89: Viral infections of the central nervous system
    
    - A92-A99: Arthropod-borne viral fevers and viral haemorrhagic fevers
    
    - B00-B09: Viral infections characterized by skin and mucous membrane lesions
    
    - B15-B19: Viral hepatitis
    
    - B20-B24: Human immunodeficiency virus
    
    - B25-B34: Other viral diseases
    
    - B35-B49: Mycoses
    
    - B50-B64: Protozoal diseases
    
    - B65-B83: Helminthiases
    
    - B85-B89: Pediculosis, acariasis, and other infestations
    
    - B90-B94: Sequelae of infectious and parasitic diseases
    
    - B95-B98: Bacterial, viral, and other infectious agents
    
    - B99: Other and unspecified infectious diseases
:::

\newpage

# Emergency Presentations

```{r, include = FALSE}
# ------------------------------------------------------------------------------
# Emergency presentations - infectious and parasitic diseases
# Data from PHIDU Social Health Atlas
# ------------------------------------------------------------------------------
# Read in PHIDU data
emergency_infectious <- f_read_phidu_iare_hospital(data_sheet    = "ED_total",
                                                   column_select = "emergency_department_presentations_total_presentations_for_certain_infectious_and_parasitic_diseases_aboriginal_people")

# Data wrangling
emergency_infectious <- emergency_infectious %>% 
  dplyr::mutate(iare_name = factor(iare_name, levels = iare_inc_vic_lvl)) %>% 
  #
  dplyr::arrange(iare_name)
```


```{r}
#
results <- list()

data <- emergency_infectious %>% 
  dplyr::rename(n     = hospital_n,
                rate  = hospital_rate,
                ratio = hospital_ratio)

results$rank_n <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::select(iare_name,
                n)

results$rank_rate <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(rate)) %>% 
  dplyr::select(iare_name,
                rate)

results$rank_ratio <- data %>% 
  dplyr::filter(iare_name %in% iare_names) %>% 
  dplyr::arrange(desc(ratio)) %>% 
  dplyr::select(iare_name,
                ratio)
```

::: {custom-style="Dotpt"}
- Data for this indicator were obtained from the PHIDU Social Health Atlas, compiled from the AIHW National Non-Admitted Patient Emergency Department Care Database.

- Between 01 July 2019 and 30 June 2020 there were 812 emergency department presentations for infectious and parasitic diseases for Aboriginal and/or Torres Strait Islander people living in Greater Melbourne.

- The number of presentations for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 108 (Northcote/Preston/Whittlesea IARE) to 8 (Whitehorse IARE).

- The age-standardised rate of presentations for Aboriginal and/or Torres Strait Islander people living in different IAREs within the NEPHU catchment ranged from 3,905 per 100,000 population (Melbourne/Port Phillip IARE) to 1,708 per 100,000 population (Melbourne East IARE).

- 5 of the 10 IAREs in the NEPHU catchment area had an age-standardised presentation rate above the average for all Aboriginal and/or Torres Strait Islander people living in Greater Melbourne (Melbourne/Port Phillip, Melbourne North-East, Maroondah, Northcote/Preston/Whittlesea, and Moreland/Broadmeadows IAREs).
:::

\newpage

```{r}
# Figure 10K-30
f_caption_figure("(A) Number and (B) age-standardised rate (per 100,000 population) of emergency department presentations for infectious and parasitic diseases for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2019 to 30 June 2020")

figure_number <- emergency_infectious %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "No",
               y_variable = hospital_n,
               y_max      = NA,
               y_breaks   = 20,
               y_expand   = 15,
               y_title    = "Number of presentations",
               plot_tag   = "A")

figure_rate <- emergency_infectious %>%
  dplyr::filter(iare_name %in% iare_names) %>% 
  #
  f_graph_iare(suppress   = "No",
               y_variable = hospital_rate,
               y_max      = NA,
               y_breaks   = 500,
               y_expand   = 175,
               y_title    = "Age-standardised rate",
               plot_tag   = "B")

figure_number + figure_rate
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

- Presentations for 'infectious and parasitic diseases' are defined as those with a principal diagnosis code between A00-B99, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en). The following major categories are included:

    - A00-A09: Intestinal infectious diseases
    
    - A15-A19: Tuberculosis
    
    - A20-A28: Certain zoonotic bacterial diseases
    
    - A30-A49: Other bacterial diseases
    
    - A50-A64: Infections with a predominantly sexual mode of transmission
    
    - A65-A69: Other spirochaetal diseases
    
    - A70-A74: Other diseases caused by chlamydiae
    
    - A75-A79: Rickettsioses
    
    - A80-A89: Viral infections of the central nervous system
    
    - A92-A99: Arthropod-borne viral fevers and viral haemorrhagic fevers
    
    - B00-B09: Viral infections characterized by skin and mucous membrane lesions
    
    - B15-B19: Viral hepatitis
    
    - B20-B24: Human immunodeficiency virus
    
    - B25-B34: Other viral diseases
    
    - B35-B49: Mycoses
    
    - B50-B64: Protozoal diseases
    
    - B65-B83: Helminthiases
    
    - B85-B89: Pediculosis, acariasis, and other infestations
    
    - B90-B94: Sequelae of infectious and parasitic diseases
    
    - B95-B98: Bacterial, viral, and other infectious agents
    
    - B99: Other and unspecified infectious diseases
:::

```{r}
# Table 10K-16
f_caption_table("Emergency department presentations for infectious and parasitic diseases for people who identified as Aboriginal and/or Torres Strait Islander, NEPHU catchment, by IARE, 01 July 2019 to 30 June 2020")

emergency_infectious %>% 
  dplyr::select(-iare_name_short) %>% 
  #
  dplyr::mutate(hospital_rate  = round(hospital_rate, digits = 0),
                hospital_ratio = round(hospital_ratio, digits = 1)) %>% 
  #
  f_table_iare(table_headers = c("Number of\npresentations", "Age-standardised rate\n(per 100,000)", "Standardised\nratio"),
               last_column   = 4) %>% 
  #
  flextable::width(j = 3,
                   width = 1.75)
```

#### Data notes:

::: {custom-style="Footnotes"}
`r knitr::asis_output(note_data_phidu_vaed)`

`r knitr::asis_output(note_caveat_underidentification)`

`r knitr::asis_output(note_caveat_iare_nephu)`

`r knitr::asis_output(note_caveat_admissions)`

`r knitr::asis_output(note_caveat_iare_ratio)`

- Presentations for 'infectious and parasitic diseases' are defined as those with a principal diagnosis code between A00-B99, coded using [ICD-10-AM](https://icd.who.int/browse10/2019/en). The following major categories are included:

    - A00-A09: Intestinal infectious diseases
    
    - A15-A19: Tuberculosis
    
    - A20-A28: Certain zoonotic bacterial diseases
    
    - A30-A49: Other bacterial diseases
    
    - A50-A64: Infections with a predominantly sexual mode of transmission
    
    - A65-A69: Other spirochaetal diseases
    
    - A70-A74: Other diseases caused by chlamydiae
    
    - A75-A79: Rickettsioses
    
    - A80-A89: Viral infections of the central nervous system
    
    - A92-A99: Arthropod-borne viral fevers and viral haemorrhagic fevers
    
    - B00-B09: Viral infections characterized by skin and mucous membrane lesions
    
    - B15-B19: Viral hepatitis
    
    - B20-B24: Human immunodeficiency virus
    
    - B25-B34: Other viral diseases
    
    - B35-B49: Mycoses
    
    - B50-B64: Protozoal diseases
    
    - B65-B83: Helminthiases
    
    - B85-B89: Pediculosis, acariasis, and other infestations
    
    - B90-B94: Sequelae of infectious and parasitic diseases
    
    - B95-B98: Bacterial, viral, and other infectious agents
    
    - B99: Other and unspecified infectious diseases
:::

